\section[Mechanical \& Practical]{Mechanical \&\\ Practical}

This category represents hands-on skills—those tied to tools, craftsmanship, infiltration, or practical know-how. These abilities are essential for characters who repair machines, break into vaults, forge identities, or create things from scratch. Whether you’re a master thief, a back-alley medic, or a steampunk inventor, these skills let you manipulate the physical world and navigate its many locks, levers, and loopholes.

Mechanical \& Practical skills are vital in heists, engineering puzzles, or settings that feature complex devices, from arcane mechanisms to bleeding-edge tech.


\subsection{Alchemy}\index{Alchemy!Skill}\index{Skills!Alchemy}\label{skill:alchemy}
\textbf{Settings:} Fantasy, Steampunk, Occult\\
\textbf{Scope:} Narrow\\
\textbf{Other Names:} \emph{Potion-Making}, \emph{Transmutation}, \emph{Elemental Chemistry}\\
\vspace{\baselineskip}

\emph{Alchemy} is a specialised branch of \emph{Crafts} focused on the creation of potions, elixirs, transmuted substances, and volatile mixtures. It involves rare ingredients, complex formulas, and precise rituals to produce supernatural or quasi-scientific effects.

Whether brewing a healing tincture, distilling a truth serum, or crafting a smoke bomb from enchanted root ash, this skill governs the crafting of consumables with magical or pseudoscientific properties.

\vspace{0.5\baselineskip}
\noindent\textbf{Requires:} \emph{Crafts} (p. \pageref{skill:crafts})


\subsection{Arcane Mechanics}\index{Arcane Mechanics!Skill}\index{Skills!Arcane Mechanics}\label{skill:arcane-mechanics}
\textbf{Settings:} Steampunk, Fantasy, Sci-Fi\\
\textbf{Scope:} Narrow\\
\textbf{Other Names:} \emph{Magitech}, \emph{Runework}, \emph{Enchanted Devices}\\
\vspace{\baselineskip}

\emph{Arcane Mechanics} is the skill of designing, repairing, and manipulating machines that incorporate magical or supernatural elements. This includes runed gearboxes, self-winding spell engines, levitating platforms, or sentient constructs powered by bound spirits.

Characters with this skill can blend craftsmanship with mysticism or advanced science. They might build mechanical familiars, rig magical traps, or troubleshoot unstable fusion-crystal cores.

\vspace{0.5\baselineskip}
\noindent\textbf{Requires:} \emph{Crafts} (p. \pageref{skill:crafts})



\subsection{Burglary}\index{Burglary!Skill}\index{Skills!Burglary}\label{skill:burglary}
\textbf{Settings:} All\\
\textbf{Scope:} Broad\\
\textbf{Other Names:} \emph{Infiltration}, \emph{Breaking and Entering}, \emph{Security Bypass}\\
\vspace{\baselineskip}

\emph{Burglary} is the skill of getting into places you're not supposed to be. It includes picking locks, disabling alarms, bypassing security systems, and sneaking into buildings without being noticed. It’s used to case targets, choose the right moment to strike, and disappear before anyone knows you were there.

Characters with high \emph{Burglary} are often scouts, thieves, or spies who thrive in urban shadows and behind locked doors. This skill may also be used to detect and exploit weaknesses in someone else's defences.

\vspace{0.5\baselineskip}
\noindent\textbf{Related Skills:} \emph{Stealth} (p. \pageref{skill:stealth}), \emph{Disguise} (p. \pageref{skill:disguise}), \emph{Technology} (p. \pageref{skill:technology})


\subsection{Crafts}\index{Crafts!Skill}\index{Skills!Crafts}\label{skill:crafts}
\textbf{Settings:} All\\
\textbf{Scope:} Broad\\
\textbf{Other Names:} \emph{Tinkering}, \emph{Repair}, \emph{Build}\\
\vspace{\baselineskip}

\emph{Crafts} is the skill of building, repairing, and modifying physical objects. This includes working with wood, metal, stone, fabric, and basic mechanical systems. Characters may forge weapons, repair gear, or cobble together makeshift tools in the field.

In more advanced or fantastical settings, \emph{Crafts} can also include clockwork mechanisms, steampunk gadgets, or low-level magical craftsmanship. This skill complements \emph{Engineering} or \emph{Arcane Mechanics} when precision or complexity increases.

\vspace{0.5\baselineskip}
\noindent\textbf{Base of:} \emph{Engineering} (p. \pageref{skill:engineering}), \emph{Arcane Mechanics} (p. \pageref{skill:arcane-mechanics}), \emph{Alchemy} (p. \pageref{skill:alchemy})
\noindent\textbf{Related Skills:} \emph{Engineering} (p. \pageref{skill:engineering}), \emph{Resources} (p. \pageref{skill:resources})



\subsection{Disguise}\index{Disguise!Skill}\index{Skills!Disguise}\label{skill:disguise}
\textbf{Settings:} All\\
\textbf{Scope:} Narrow\\
\textbf{Other Names:} \emph{Costuming}, \emph{Alter Ego}, \emph{Masquerade}\\
\vspace{\baselineskip}

\emph{Disguise} is the skill of altering one’s appearance to impersonate someone else or avoid recognition. It includes makeup, costume, posture, voice control, and other techniques used to blend in or adopt a new identity.

This skill is useful in espionage, infiltration, or social subterfuge, especially when paired with \emph{Deceive}. In fantasy or sci-fi settings, it may also involve glamours or holographic concealment.

\vspace{0.5\baselineskip}
\noindent\textbf{Requires:} \emph{Deceive} (p. \pageref{skill:deceive})



\subsection{Engineering}\index{Engineering!Skill}\index{Skills!Engineering}\label{skill:engineering}
\textbf{Settings:} Modern, Sci-Fi, Steampunk\\
\textbf{Scope:} Narrow\\
\textbf{Other Names:} \emph{Structural Design}, \emph{Mechanics}, \emph{Applied Physics}\\
\vspace{\baselineskip}

\emph{Engineering} is the application of scientific and mathematical principles to the construction and optimisation of complex systems. It covers the design of buildings, vehicles, engines, infrastructure, and advanced mechanical devices. Unlike \emph{Crafts}, which focuses on hands-on creation, \emph{Engineering} emphasises planning, load-bearing analysis, and systems integration.

Characters with this skill may draft blueprints, analyse weaknesses in structures, or construct bridges and siege engines. In high-tech or steampunk settings, this skill governs the construction of automatons, airships, or massive arcane reactors.

\vspace{0.5\baselineskip}
\noindent\textbf{Requires:} \emph{Crafts} (p. \pageref{skill:crafts})




\subsection{Forgery}\index{Forgery!Skill}\index{Skills!Forgery}\label{skill:forgery}
\textbf{Settings:} Crime, Urban, Political, Espionage\\
\textbf{Scope:} Narrow\\
\textbf{Other Names:} \emph{Counterfeiting}, \emph{Falsification}, \emph{Forgery Arts}\\
\vspace{\baselineskip}

\emph{Forgery} is the skill of replicating documents, signatures, artwork, seals, or other official markings. It includes knowledge of inks, paper, historical styles, and bureaucratic procedures—anything needed to pass off a fake as the real thing.

Characters with this skill can create false IDs, fake royal decrees, or alter written evidence. Forgery may also be used to spot forged items made by others.

\vspace{0.5\baselineskip}
\noindent\textbf{Requires:} \emph{Deceive} (p. \pageref{skill:deceive})



\subsection{Resources}\index{Resources!Skill}\index{Skills!Resources}\label{skill:resources}
\textbf{Settings:} All\\
\textbf{Scope:} Broad\\
\textbf{Other Names:} \emph{Wealth}, \emph{Holdings}, \emph{Assets}\\
\vspace{\baselineskip}

\emph{Resources} is the skill of having material wealth, social capital, and access to goods or services. It determines whether you can afford to bribe a guard, purchase rare components, hire help, or maintain a lifestyle that commands respect. This skill can be used to acquire things quickly, legally or not, without needing to roll for contacts or crafting.

Characters with high \emph{Resources} might be nobles, merchants, investors, or savvy street-level fixers. They may not carry a toolkit—but they can afford someone who does.

\vspace{0.5\baselineskip}
\noindent\textbf{Related Skills:} \emph{Contacts} (p. \pageref{skill:contacts}), \emph{Crafts} (p. \pageref{skill:crafts})



\subsection{Technology}\index{Technology!Skill}\index{Skills!Technology}\label{skill:technology}
\textbf{Settings:} Modern, Sci-Fi, Cyberpunk, Supernatural-Tech\\
\textbf{Scope:} Broad\\
\textbf{Other Names:} \emph{Computers}, \emph{Hacking}, \emph{Digital Systems}\\
\vspace{\baselineskip}

\emph{Technology} is the skill of understanding, using, and manipulating digital systems, electronics, and advanced devices. It includes tasks like hacking security systems, reprogramming AIs, bypassing digital locks, configuring sensor arrays, or interfacing with alien consoles.

Unlike \emph{Crafts}, which focuses on physical tools and traditional mechanics, \emph{Technology} governs information systems, modern automation, and the invisible infrastructure of the digital world.

Characters with high \emph{Technology} might be hackers, technomancers, engineers, drone pilots, or cybernetic experts.

\vspace{0.5\baselineskip}
\noindent\textbf{Related Skills:} \emph{Engineering} (p. \pageref{skill:engineering})