\begin{NPC}[%
    name=Anchor Guardian,%
    description=Protector of the Celestial Anchor%
  ]{Anchor Guardian}
  
  \emph{It is not alive, but it remembers how to kill.}
  
  \subsubsection*{Background:}
  Forged long ago by the Celestine Host, the Anchor Guardian was designed to defend sacred astronomical relics against theft or desecration. It was never meant to be reactivated—but the Lunar Remnant has reignited it using unstable starfire. It now functions as the last line of defence before the Celestial Anchor can be destroyed.
  
  It levitates in battle, partially phased between this world and moonlight. Rings of glowing orrery arms rotate around it, cutting through the air and deflecting spells. It does not speak. It shines.
  
  \vspace{0.5\baselineskip}
  
  \begin{SkillsBox}
    \Expert & Slash with Spinning Ring Blades \\
    \Skilled & Redirect Incoming Spells, Hover Over Hazardous Terrain \\
    \Novice & Track Targets by Heat Signature, Resist Disruption, Shatter Cover with Force \\
  \end{SkillsBox}
  
  \begin{SkillsBox}[Spells]
    \Skilled & Starburst Convergence (p. \pageref{spell:starburst-convergence}) \\
    \Novice & Lunar Flare Pulse (p. \pageref{spell:lunar-flare-pulse}) \\
  \end{SkillsBox}
  
  \ManaBox
  
  \begin{TraitsBox}
    \item[Celestial Core] — Immune to charm, fear, and fatigue. Reduces all non-magical damage by 1.
    \item[Orbital Defence Matrix] — Once per round, may deflect one ranged or magical attack unless the attacker overcomes a DL 3 challenge.
    \item[Overload Cascade] — When reduced to half health, the Guardian’s spells increase in level by +1 until destroyed.
  \end{TraitsBox}
  
  \DamageBox
  
  \end{NPC}

