\documentclass[nodeprecatedcode,bg=print]{dndbook}
\usepackage{wyrd}
\raggedright
\pagestyle{empty}

\begin{document}
\Large
\textbf{Welcome to The Grand Casebook}

London, 1896. A city of gaslit streets, towering factories, and secrets lurking in the shadows. This is an era of progress, where steam and steel reshape the world—but beneath the veneer of industry and refinement, the old mysteries remain. The line between science and the supernatural is thinner than most would dare to believe.

You are part of \textbf{The Grand Society of Inquiry}, a clandestine organization of detectives, scholars, and unconventional thinkers dedicated to unraveling the mysteries the world would rather forget. The police may handle the mundane crimes, but when the case is impossible, when the authorities turn a blind eye, or when the answers defy reason, that is where you come in.

The aristocracy hides more than it reveals. The city’s underworld knows whispers of truths the elite wish buried. Strange happenings unfold in laboratories, occult circles, and long-forgotten ruins. It is your job to investigate, to bring truth to light—whether the world is ready for it or not.

You will encounter murderers whose motives defy logic, inventions beyond their time, secret societies vying for power, and horrors that exist just beyond the veil of reason. Some mysteries should never be solved, but you have chosen to chase the truth regardless.

London may not thank you for what you uncover. The truth is rarely comforting. But if not you, then who?

So, tell me: \textbf{What mystery has found its way to your doorstep tonight?}


\end{document}
