\begin{WyrdScenarioHeading}[Taxed to the Max]{Taxed to the Max:\\ The IRS Comes Knocking}
    \label{scenario:taxed-to-the-max}
    \index{Taxed to the Max}
    \index{Scenario!Taxed to the Max}

    Trouble arrives in a crisp navy blazer and orthopedic shoes. Agent Dolores “The Hawk” Hawkins of the IRS has rolled into Dusty Pines with a government-issued briefcase and a mission: collect on years of back taxes owed by one of the residents (possibly one of the players). But as Dolores digs into the park’s suspicious finances and weirdly annotated receipts, the rest of Dusty Pines starts panicking.

    Rumors swirl that Dolores isn’t just a tax agent—some claim she’s a supernatural enforcer or a hunter of magical loopholes. Whether mortal or mythic, she’s too good at her job, and her questions are getting far too close to the truth. The players must dodge her inquiries, hide incriminating evidence, and possibly even confront the growing possibility that Dolores is here for something much stranger than unpaid income.

    \subsection*{Premise}
    One of the players has (understandably) neglected their taxes, and now an IRS agent is knocking. But Agent Hawkins isn’t just here to audit—she’s unraveling secrets that Dusty Pines can't afford to expose. The players must protect their friend, the park’s oddball magic, and maybe their own freedom before she brings the hammer (and itemized forms) down.

    \subsection*{Goals for the Players}
    \begin{itemize}
        \item Avoid Dolores’ questioning and prevent her from discovering magical irregularities.
        \item Bury or “correct” any incriminating records—including suspicious magical expenses.
        \item Uncover Dolores’ true intentions and whether she’s just IRS… or something more.
    \end{itemize}

    \subsection*{Atmosphere \& Tone}
    This scenario blends bureaucratic comedy, magical misdirection, and paranoia. Think \textit{Catch Me If You Can} meets a supernatural episode of \textit{Brooklyn Nine-Nine}. Players should feel the tension of hiding the truth while also being tempted to out-bureaucrat the bureaucrat. Mix in magical receipts, shady accountants, and maybe a little interdimensional tax law.
\end{WyrdScenarioHeading}

The sun rises over Dusty Pines with suspiciously precise timing—7:02 a.m. exactly—just as a spotless black sedan rolls to a stop outside the park office. A tall, stiff-backed woman in a navy-blue suit steps out, clutching a reinforced briefcase and a thermos labeled “Audit Fuel.” This is \textbf{Agent Dolores “The Hawk” Hawkins}, and she has arrived with purpose.

Rumor spreads fast: someone in Dusty Pines is under federal investigation for back taxes. And not just any taxes—\textit{deeply confusing, questionably magical taxes}. As the trailer park braces for impact, one thing becomes clear: the players will need to outwit, outmaneuver, and out-audit the IRS… or risk losing far more than a few deductions.

\subsection{The Audit Begins}

A flyer appears overnight on several trailers—not tacked up, but neatly slid under doors and magically laminated. It reads:

\begin{center}
    \fbox{\parbox{0.9\linewidth}{
        \centering
        \textbf{\Large INTERNAL REVENUE SERVICE FIELD AUDIT NOTICE}\\
        \smallskip
        \textbf{To: [Insert Player Name]}\\
        \textbf{Subject: Discrepancies in Declared Income, Schedule M13}\\
        Please report to the Park Office at 10:00 a.m. sharp. Bring all records, receipts, familiars, and/or dimensional deduction forms. No pets. No hexes. No excuses.
    }}
\end{center}

\subsubsection*{At the Park Office}
Bobby “the Befuddled” Barkins is in full panic mode, clutching a pencil stub and a half-completed “Emergency Tax Ritual Worksheet.” The office smells like burnt sage and copier toner.

Agent Hawkins is already there, standing perfectly still, reviewing documents that weren’t supposed to exist. She speaks in clipped sentences and never looks away for more than a second.

\textbf{What Happens}
\begin{itemize}
    \item She has a thick dossier on the target player—one that includes suspicious income streams (e.g., “Artifact Retrieval Fees,” “Potion Reimbursements,” “Cursed Duck Disposal”).
    \item Dolores begins her interrogation politely but with relentless precision. She asks about forms the player has definitely never seen.
    \item She notices anything odd about the trailer park — strange architecture, unnatural lighting, talking raccoons, etc.—and notes it without comment.
    \item She asks to “inspect” the player’s trailer.
\end{itemize}

\textbf{What the Players Can Do}
\begin{itemize}
    \item Redirect her attention with magical bureaucracy—perhaps invoking obscure (possibly fake) supernatural tax codes.
    \item Call in Lyle “The Tax Ghost” Gerber for professional help… at their own risk.
    \item Begin quietly destroying or hiding anything that could be construed as tax fraud or magical activity.
\end{itemize}

\begin{CommentBox}{Optional Escalation}
    If the player is evasive or openly suspicious, Dolores declares a \textbf{park-wide random audit}, putting everyone under the microscope. Cue widespread panic and impromptu receipt-forging parties.
\end{CommentBox}

\end{multicols}
\clearpage
\begin{multicols}{2}

\begin{NPC}[description={IRS Agent, Bureaucratic Bloodhound,\\ Possibly Supernatural}]{Agent Dolores “The Hawk” Hawkins}

    Dolores Hawkins is the IRS’s finest field agent, known for her unnerving ability to appear where she's least expected—and for never letting a deduction slip by unnoticed. Whether she’s just a terrifyingly competent civil servant or something… more… remains up for debate. What’s certain is that she won’t leave Dusty Pines without answers.

    \textbf{Appearance:} Immaculate navy-blue suit, steel-grey bun, and unsettlingly sharp eyes. Her clipboard may or may not be enchanted.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Expert & \textbf{Investigation}, \textbf{Will} \\
        \Skilled & \textbf{Provoke}, \textbf{Lore} \\
        \Novice & \textbf{Notice}, \textbf{Empathy}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Audit Sense] Once per scene, Dolores may “just know” where something incriminating is hidden. Treat as a +2 bonus to any Investigation action.
        \item[Bureaucratic Shielding] Anyone trying to use direct magic on Dolores must succeed on a \textbf{Will} \DL{+2} check or have the spell bounce off her “paperwork aura.”
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=3,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}
\begin{NPC}[description={Spectral Accountant, Shady Consultant,\\ Financial Necromancer?}]{Lyle “The Tax Ghost” Gerber}

    Lyle Gerber was once a mid-level accountant who vanished during a suspicious audit involving five shell companies, a haunted casino, and something called “The 1099 Phantasm Loop.” Now, he haunts spreadsheets and appears wherever tax evasion takes on metaphysical proportions. Lyle insists he's not dead, just “off the books,” and claims to help people “navigate the grey areas of magical finance.” In reality, he’s wildly unreliable, questionably magical, and absolutely the kind of ghost who still charges consulting fees.

    \textbf{Appearance:} Transparent green visor, ghostly suspenders, and an incorporeal pocket calculator that spits out glowing tape. Smells faintly of burnt receipts.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Expert & \textbf{Deceive}, \textbf{Lore} \\
        \Skilled & \textbf{Rapport}, \textbf{Burglary} \\
        \Novice & \textbf{Notice}, \textbf{Will}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Phantom Filing] Once per session, Lyle can conjure a tax record or deduction from the spirit world—believable, but possibly cursed.
        \item[Off the Books] Lyle is immune to most magical detection or truth spells… but only as long as he’s being paid.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=2,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}


\end{multicols}
\clearpage
\begin{multicols}{2}


\subsection{Cook the Books, or Bury Them}

Once Dolores starts asking around, panic spreads. Residents who haven’t filed a tax form since the Reagan administration begin rifling through shoe boxes, junk drawers, and cursed vaults in search of receipts. The players must move fast to prevent Dolores from uncovering anything truly damning—magical or otherwise.

\subsubsection*{The Problem}
The park is full of financial irregularities:
\begin{itemize}
    \item Tito the chupacabra once got paid in rotisserie chickens.
    \item Edna sells “services” without reporting income (especially the ones involving frogs).
    \item A certain player has been writing off “emotionally significant crystals” as business deductions.
\end{itemize}

\subsubsection*{The Players’ Options}
\begin{itemize}
    \item \textbf{Destroy the Evidence}: Shred, burn, or “accidentally banish” tax forms. (Requires \textbf{Stealth}, \textbf{Burglary}, or chaotic magic \DL{+1})
    \item \textbf{Forge Deductions}: Backdate and fill out believable forms to explain income. (Requires \textbf{Deceive}, \textbf{Crafts}, or \textbf{Lore} \DL{+2})
    \item \textbf{Distract Dolores}: One player lures Dolores into a painfully long HOA-style community tour while the others clean house.
\end{itemize}

\subsubsection*{Potential Obstacles}
\begin{itemize}
    \item A magical receipt book animates and starts loudly reciting every undocumented purchase the players have ever made.
    \item One NPC (perhaps Rusty or Bobby) tries to “help” by inventing increasingly absurd cover stories that only make things worse.
    \item Dolores discovers a suspicious locked cabinet labeled “Definitely Not Hidden Tax Records.” She will try to open it unless convinced otherwise.
\end{itemize}

\begin{CommentBox}{If They Fail}
    If Dolores finds enough discrepancies, she escalates to \textbf{Phase Two: Forensic Interviewing}… and that’s when things start getting truly weird.
\end{CommentBox}

\subsection{Phase Two: Forensic Interviewing}

If the players fail to sufficiently dodge, deceive, or distract Dolores, she escalates to Phase Two: private interviews, magical lie detection, and reality-checking rituals.

\subsubsection*{What This Looks Like}
\begin{itemize}
    \item She summons players one by one to a conjured IRS cube—a sterile interview space where spells like \textbf{Truth Tagging} and \textbf{Deduction Projection} are active.
    \item Dolores uses enchanted ledgers to compare verbal answers to cosmic tax records (which somehow exist for everyone).
    \item She asks piercing, deeply personal questions like “Have you ever used a glamour to avoid sales tax?” or “Please list all known income streams, including spectral currencies.”
\end{itemize}

\subsubsection*{Ways to Resist}
\begin{itemize}
    \item Use \textbf{Will} to withstand her magical scrutiny.
    \item Invoke a legal loophole using obscure magical bureaucracy—possibly with help from Lyle the Tax Ghost.
    \item Create magical static (via enchanted paperwork or spell-scroll shredders) to scramble her audit spells.
\end{itemize}

\subsubsection*{If She Succeeds}
Dolores begins writing up full magical citations and may start seizing “noncompliant property”—which could include familiars, charms, or entire trailers.

\begin{CommentBox}{Tone Note}
    This phase should feel like a magical interrogation combined with an absurd, deadpan HR meeting. Think Kafka meets Dungeons \& Dragons: Office Edition.
\end{CommentBox}


\subsection{A Visit from the Tax Ghost}

It’s late afternoon when the temperature in the communal laundry trailer suddenly drops. The lint in the corner begins swirling into unnatural patterns. Then, with a crackle of spectral receipts and the distant ding of a calculator tape, \textbf{Lyle “The Tax Ghost” Gerber} materialises.

\subsubsection*{His Entrance}
Lyle floats two inches above the floor, translucent and mildly smug.

\begin{Example}{Lyle’s Introduction}
    “I heard someone was in tax trouble… and that’s my cue. Don’t worry—I’m here to help. For a modest fee, of course. Ghosts gotta eat too… metaphorically.”
\end{Example}

\subsubsection*{What He Offers}
Lyle claims to have several "solutions" for the players:
\begin{itemize}
    \item \textbf{“Ghost Expenses”}: He can generate spectral deduction forms that “technically exist,” usable for creative write-offs like “exorcism costs” and “spiritual hazard pay.”
    \item \textbf{“Temporal Sheltering”}: He offers to shift one player’s trailer five minutes out of sync with reality to dodge the audit window.
    \item \textbf{“Phantom Filing Services”}: A single-use spell that creates a completed tax return—albeit one that may summon an IRS shade if mishandled.
\end{itemize}

\subsubsection*{Complications}
\begin{itemize}
    \item Lyle’s paperwork sometimes screams. Literally.
    \item He charges “a cut” of any magical items used to hide evidence.
    \item If questioned too hard, Lyle will vanish mid-sentence and return hours later with even worse ideas.
\end{itemize}

\begin{CommentBox}{Fun Consequence}
    If the players use one of Lyle’s deduction tricks, Dolores may briefly detect something “wrong” in the records—but it disappears when checked, leaving her unnerved but more determined than ever.
\end{CommentBox}


\subsection{Park-Wide Panic}

Once Dolores expands her audit to include the entire trailer park (either due to failed player attempts to stall her or “suspicious patterns in the magical income matrix”), the residents of Dusty Pines lose their collective minds.

\subsubsection*{What It Looks Like}
Picture a supernatural tax apocalypse:
\begin{itemize}
    \item Bobby is frantically stuffing paperwork into a portable rift disguised as a filing cabinet.
    \item Edna is trying to enchant receipts with emotional significance so they become “non-taxable memories.”
    \item Tito the chupacabra has vanished—leaving behind a suspiciously perfect tax form labeled “No Comment.”
    \item The enchanted port-a-potty from earlier scenarios is offering bribes to keep its plumbing business off the books.
    \item Rusty the Gnome Whisperer has declared his lawn a “tax-exempt micronation,” complete with passport stamps.
\end{itemize}

\subsubsection*{Player Goals}
This is a semi-freeform chaos scene where players may:
\begin{itemize}
    \item Help other residents fudge records, forge magical documents, or banish enchanted ledgers that won’t stop tattling.
    \item Organise a “Distraction Festival” — maybe an impromptu community potluck with suspiciously convenient timing.
    \item Locate Dolores' car and replace her audit scrolls with decoys. (Requires \textbf{Burglary} or \textbf{Deceive} \DL{+2})
    \item Calm down residents who are panicking, turning invisible, or summoning protective familiars with law degrees.
\end{itemize}

\subsubsection*{Complications}
\begin{itemize}
    \item One trailer has already been “confiscated” by the audit — it's frozen in a glowing stasis cube labeled “Assets Under Review.”
    \item A magical form has gone rogue and started self-replicating. It’s trying to audit Bobby’s cat for “fish-related earnings.”
    \item Lyle returns in the middle of the chaos, offering to “take the audit to court,” but he’s just wearing a sheet and yelling legal jargon.
\end{itemize}

\begin{CommentBox}{Tone Note}
    This scene should lean fully into absurd magical bureaucracy. Think wizardly tax panic + community theatre-level misdirection. Let players get creative—and let failure be funny, not punishing.
\end{CommentBox}



\subsection{Digging into Dolores}

Between the paperwork storms and spectral calculators, something just doesn’t sit right. Dolores is clearly more than a simple IRS agent, and her arrival was just a little too well-timed. If the players take the initiative to look deeper into her background, they may uncover secrets even the government doesn’t know about.

\subsubsection*{Ways to Investigate}
\begin{itemize}
    \item \textbf{Consult Edna:} Edna, of course, “might know something”—if the players bring her a cursed checkbook or agree to sit through her seminar on magical budgeting. A successful \textbf{Lore} or \textbf{Rapport} \DL{+1} reveals that Dolores might be part of an ancient order of magical auditors, originally designed to monitor sorcery-related debts to the Fae courts.
    
    \item \textbf{Check Her Credentials:} A \textbf{Notice} or \textbf{Investigate} \DL{+2} check while Dolores is distracted might reveal her badge occasionally glitches—flickering between IRS, MARC (Magical Accounting \& Revenue Command), and a long-defunct Department of Interplanar Rebalancing.

    \item \textbf{Ask Lyle (Carefully):} If Lyle is still around, he may nervously admit that Dolores “isn’t just after taxes, if you catch my drift.” He implies she’s gathering enough evidence to petition for a full \textbf{Magical Containment Designation} on Dusty Pines—a bureaucratic move that would put the entire park under permanent federal quarantine.
\end{itemize}

\subsubsection*{What They Might Discover}
\begin{itemize}
    \item \textbf{Dolores is on a Trial Assignment:} This audit is part of a test run. If successful, she may be promoted to “Arcane Enforcement Tier II” and given greater powers.
    \item \textbf{The Audit is a Cover:} Her primary mission isn’t just taxes—it’s to identify magical “unregistered anomalies.” If she finds enough evidence, she’ll trigger a lockdown and call in the Department of Dimensional Oversight.
    \item \textbf{She Has Doubts:} While Dolores won’t admit it, she’s quietly impressed by the weird community spirit of Dusty Pines. A successful \textbf{Empathy} \DL{+2} during conversation might reveal a moment of hesitation—she’s tired of chasing monsters and might be open to persuasion.
\end{itemize}

\begin{CommentBox}{Player Advantage}
    If the players gather any of this information, they gain a powerful bargaining chip. They may now:
    \begin{itemize}
        \item Confront Dolores with her hidden motives to stall the audit.
        \item Appeal to her personal doubts and convince her Dusty Pines doesn’t need regulation.
        \item Threaten to file a grievance with the Interplanar Oversight Board (real or not).
    \end{itemize}
\end{CommentBox}

\subsection{Final Confrontation: Balancing the Books}

With the park in chaos, magical paperwork fluttering through the air, and every receipt spiritually vibrating with stress, it’s time for the players to make their final move. Dolores stands in the centre of the trailer park with her enchanted audit ledger glowing like a doomsday tome.

\subsubsection*{How the Confrontation Can Go}
The players must now use what they’ve gathered—be it leverage, lies, empathy, or magical legalese—to get Dolores off their backs.

\paragraph{Option 1: The Appeal to Bureaucratic Humanity}
If the players uncovered her secret doubts, they can attempt a heartfelt plea:
\begin{itemize}
    \item Highlight how the park is weird but self-sufficient.
    \item Emphasise how Dolores deserves a case that isn’t a trap disguised as a promotion.
    \item Offer her honorary membership in the Dusty Pines HOA (Harmless Oddities Alliance).
\end{itemize}
\textbf{Empathy} \DL{+2} or \textbf{Rapport} \DL{+1} succeeds.

\paragraph{Option 2: Leverage the Hidden Truth}
If the players uncovered her ties to the Magical Accounting \& Revenue Command or the Department of Dimensional Oversight:
\begin{itemize}
    \item Accuse her of overstepping her authority—this isn’t a MARC-approved operation.
    \item Threaten to contact interplanar regulators or expose her “extra-planar jurisdiction.”
\end{itemize}
\textbf{Deceive} or \textbf{Lore} \DL{+2} succeeds, especially with forged paperwork from Lyle.

\paragraph{Option 3: Chaos Wins}
If all else fails (or intentionally escalates), the park rises up:
\begin{itemize}
    \item Bobby triggers the glitter sprinkler system.
    \item Edna throws cursed audit scrolls into her leyline-powered compost bin.
    \item The residents flood the park with magical “deductions” until Dolores’ book explodes into confetti.
\end{itemize}
This chaotic approach succeeds with a group \textbf{Will} check \DL{+2} or creative teamwork — but may cause... paperwork repercussions.

\subsubsection*{Outcome Options}

\begin{itemize}
    \item \textbf{Dolores Withdraws the Audit:} If persuaded or pressured effectively, Dolores sighs, stamps her audit scroll “INCOMPLETE” in glowing red ink, and disappears in a puff of peppermint-scented bureaucracy.
    \item \textbf{Negotiated Peace:} Dolores agrees to drop the investigation in exchange for a regular “compliance postcard” once per year. She leaves—but says she’ll be watching.
    \item \textbf{Containment Order:} If the players fail catastrophically, Dusty Pines is marked for magical containment. However, Lyle appears with a “paperwork override hex” (i.e., forged documents) and buys them time to fix it in a future scenario.
\end{itemize}

\begin{CommentBox}{If You Want to Tease Future Trouble…}
    Dolores pauses before leaving. She mutters, “Let’s hope the Department of Arcane Property Reclamation doesn’t get wind of this mess.”
\end{CommentBox}