%% FIXME: Move him to a recurrent NPC section and add a photo
\begin{WyrdFullNPC}[%
		name=Inspector Julian Hargrave,%
		description=By-the-Book Investigator,%
		float=!t%
	]{Inspector Julian Hargrave}
	
    \emph{A relentless investigator with little patience for theatrics, Inspector Hargrave believes in the cold, hard facts of an investigation—and that the law is the only true shield against chaos.}
    
    \subsubsection*{Background:}
    Inspector Hargrave has built a reputation for being thorough, methodical, and incorruptible—a rarity in London’s police force. He takes personal offence at private investigators meddling in official cases, seeing them as little more than opportunists playing detective. However, he is intelligent enough to recognise talent when he sees it, even if he resents being forced to cooperate. He is determined to bring order to every case he handles, and the Brass Orchid murder is no exception.

    \subsubsection*{Skills:}
    \begin{itemize}
       \item \Expert: Investigation
        \item \Skilled: Awareness, Will
        \item \Novice: Persuasion, Resources, Insight
    \end{itemize}
    
    \subsubsection*{Traits:}
    \begin{itemize}
        \item \textbf{The Law is My Shield} – Gains a bonus when using his authority to force cooperation or uncover evidence.
        \item \textbf{Dogged Pursuit} – Once per session, may reroll when tracking a suspect or uncovering a crucial clue.
        \item \textbf{By the Book} – Can create an advantage when leveraging official procedures to stall or control a situation.
    \end{itemize}
\end{WyrdFullNPC}

