% !TeX root = ../../../wyrd.tex


\end{multicols}

\newpage
\section{Key NPCs}

In the following pages, you will find a selection of key NPCs designed to serve as recurring figures. Each character includes a brief description, a glimpse into their background, and a set of traits that can be used to enrich their presence, deepen interactions, and support the unfolding mystery in your game.

\begin{description}
    \item[Rahjin the Ledger-Eater (page \pageref{npc:rahjin-ledger-eater})] --- A whispering debt-broker whose memory for favours owed and promises broken can topple kings.

    \item[Iszara of the Ember-Sigh (page \pageref{npc:iszara-ember-sigh})] --- A wandering Ashcraft sorceress who speaks with flame and follows omens through the burning sands.

    \item[Sazir the Forgescourge (page \pageref{npc:sazir-forgescourge})] --- A flamboyant master-smith who forges myth-forged blades and demands your story as payment.

    \item[Nahema al-Zahir (page \pageref{npc:nahema-al-zahir})] --- The charismatic envoy of the Sapphire Concord, who hires mercenaries to recover dangerous relics before empires bury the truth.

    \item[Zeyna Three-Cups (page \pageref{npc:zeyna-three-cups})] --- The no-nonsense tavernkeeper of the Scorched Fig, who hears everything and forgets nothing—unless she’s paid not to.
    
    \item[Ehvrem the Coilbound (page \pageref{npc:ehvrem-coilbound})] --- A serpent-spirit in human form who trades rare magical items in exchange for secrets, memories, or names never spoken.
\end{description}

\clearpage

\subsection{{\small Keeper of Forgotten Debts}\\ Rahjin the Ledger-Eater}
\label{npc:rahjin-ledger-eater}

\emph{He speaks softly, but always with numbers. The desert knows its debts—and Rahjin never forgets.}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    Rahjin was once a humble scribe for the Treasury of Sand, but after surviving a purge by naming every official’s secret debt aloud, he became a broker of favours, blood, and ruin. Now known as the Ledger-Eater, he walks between courts and crypts, whispering of balances unpaid. He carries no weapons—but his name alone can collapse reputations.

    He offers information, clean slates, or ruin to those who deal wisely. But every favour owed is etched into his silent ledgers, written in dust or tattooed onto skin.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Rahjin is a neutral—but dangerous—power broker. Use him to:
    \begin{itemize}\raggedright
        \item Offer rare information in exchange for future debts.
        \item Threaten players with unknown obligations tied to their pasts.
        \item Manipulate nobles, guilds, or even crime syndicates through economic whispers.
        \item Deliver cryptic warnings that turn out to be stunningly accurate.
    \end{itemize}

    He’s ideal for scenes involving deals, manipulation, or uncertain loyalties.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\textbf{+3 Calculate Leverage} \\
        \noindent\textbf{+2 Recall Names and Debts} \\
        \noindent\textbf{+2 Predict Outcomes} \\
        \noindent\textbf{+2 Calm a Crowd} \\
        \noindent\textbf{+2 Disappear into a Crowd} \\
        \noindent\textbf{+2 Appraise Hidden Worth}
    \subsubsection{Traits}
        \textbf{You Owe Me} — Once per session, name a character’s hidden debt and gain leverage over them (narrative advantage).\\
        \textbf{Unwritten Ledger} — Can recall exact words or details from past deals without ever writing them down.
\end{paracol}

\vspace{.5\baselineskip}
\hrule
\vspace{.5\baselineskip}

\subsection{{\small Ashcraft Sorceress of the Dunes}\\ Iszara of the Ember-Sigh}
\label{npc:iszara-ember-sigh}

\emph{Her eyes smoulder with stories. Her fire does not burn—it remembers.}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    Iszara was orphaned during the Fall of Ireveth, when the city’s fires never went out. She walked out of those flames untouched, speaking a name no one taught her. Now, she serves no master but flame itself.

    A rare practitioner of Ashcraft, Iszara blends memory, fire, and grief into her spells. She believes flame is a storyteller—and her role is to speak its truth through ash and ember. She has little interest in politics, but follows signs, dreams, and burning omens with alarming precision.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Iszara is a mystic guide, dangerous hermit, or flame-wielding ally. She may:
    \begin{itemize}\raggedright
        \item Appear suddenly when fire is invoked or a sacred place burns.
        \item Offer cryptic insights or dream-prophecies.
        \item Aid the players with magic—but always demand they "repay" the flame.
        \item Serve as a quest-giver tied to ancient firebound secrets.
    \end{itemize}

    She is powerful, but rarely stays in one place long.

    \switchcolumn
    \subsubsection{Skills}\raggedright
        \noindent\textbf{+3 Breathe Ashes (Ashcraft spell)} \\
        \noindent\textbf{+2 Kindle Grief (Ashcraft spell)} \\
        \noindent\textbf{+2 Speak Forgotten Names} \\
        \noindent\textbf{+2 Listen to the Fire} \\
        \noindent\textbf{+2 Walk Through Flame} \\
        \noindent\textbf{+2 Survive in the Desert Heat}
    \subsubsection{Traits}
        \textbf{Touched by Flame} — Once per scene, ignore the Magic Point cost of a +1 spell.\\
        \textbf{Ashbound Omen} — Can declare a symbolic dream or sign that predicts an event, triggering GM intervention or insight.
\end{paracol}

\subsection{{\small Master of Blades and Bids}\\ Sazir the Forgescourge}
\label{npc:sazir-forgescourge}

\emph{They say every blade Sazir makes has a story. He says that's not true—some have three.}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    A former duelist turned master weaponsmith, Sazir earned the title “Forgescourge” after defeating a rival school by crafting their ruin—literally. Now semi-retired, he maintains a smithy tucked in the molten bowels of the Ironreach, where he forges blades, bows, and bizarre contraptions from salvaged relics and cursed scrap.

    Eccentric, vain, and overly dramatic, Sazir treats every weapon as a child and every customer as an unworthy thief—until they earn his respect or make him laugh. His prices are high, but he occasionally offers “commissions” to those with stories worth forging.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Sazir is the go-to NPC for unique weapons and weird armaments. He might:
    \begin{itemize}
        \item Offer rare or enchanted gear—often flawed in poetic ways.
        \item Ask for strange components to craft a new item.
        \item Test players before agreeing to forge for them.
        \item Gift a weapon that seems useless—until it's not.
    \end{itemize}

    He's ideal for levelling up character gear in story-rich ways.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\textbf{+3 Forge Exotic Weapons} \\
        \noindent\textbf{+2 Appraise Metal by Sound} \\
        \noindent\textbf{+2 Duel with Improvised Blades} \\
        \noindent\textbf{+2 Detect Cursed Craftsmanship} \\
        \noindent\textbf{+2 Tell a Weapon’s History} \\
        \noindent\textbf{+2 Bargain with the Proud}
    \subsubsection{Traits}
        \textbf{This Blade Has Purpose} — Once per session, craft or modify a weapon to solve a current problem.\\
        \textbf{Forged in Heat, Spoken in Iron} — May reroll when intimidating or impressing others through craftsmanship.
\end{paracol}

\vspace{.5\baselineskip}
\hrule
\vspace{.5\baselineskip}

\subsection{{\small The Sapphire Concord’s Grand Envoy}\\ Nahema al-Zahir}
\label{npc:nahema-al-zahir}

\emph{She walks through ancient tombs like a queen through her gardens—and expects you to keep up.}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    Nahema leads the Sapphire Concord, a prestigious but fiercely independent organisation of scholars, adventurers, and diplomats. Their mission: to recover lost knowledge and secure dangerous relics before they fall into the wrong hands—or are erased by empires.

    Regal, brilliant, and feared in negotiation halls, Nahema brokers contracts with mercenaries and adventurers (including the player characters) to undertake missions the Concord cannot risk its own hands on. She believes in truth as a weapon—and uses it like one.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Nahema serves as a mission-giver and recurring employer. She may:
    \begin{itemize}
        \item Summon the players to retrieve or safeguard a specific relic.
        \item Offer rewards in knowledge, coin, or influence.
        \item Provide critical intel about magical threats in the world.
        \item Challenge the players' morals when truth and power collide.
    \end{itemize}

    She is principled, but not naive—and she expects results.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\textbf{+3 Command a Room} \\
        \noindent\textbf{+2 Identify Magical Relics} \\
        \noindent\textbf{+2 Negotiate without Conceding} \\
        \noindent\textbf{+2 Recall Forgotten Pacts} \\
        \noindent\textbf{+2 Mark Lies in Silence} \\
        \noindent\textbf{+2 Recruit the Unrecruitable}
    \subsubsection{Traits}
        \textbf{Voice of the Concord} — Once per scene, declare a diplomatic right or historical precedent that others must acknowledge.\\
        \textbf{The World Has Teeth} — When hiring or commanding others, Nahema may reroll if she invokes fear, truth, or legacy.
\end{paracol}

\subsection{{\small Keeper of the Scorched Fig Tavern}\\ Zeyna Three-Cups}
\label{npc:zeyna-three-cups}

\emph{"First drink’s cheap, second’s real, third's the one I ask what you’re running from."}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    Zeyna has run the Scorched Fig Tavern for thirty years. Some say she bought it with prize money from a knife-fighting championship. Others say she inherited it from a djinn she once tricked. She won’t confirm either story—but if you ask while pouring your third drink, she might wink.

    Her tavern is a gathering point for mercenaries, scholars, and relic-hunters. She knows every name worth knowing and can read a liar from the doorway. Her advice is blunt, her deals fair, and her memory unforgiving.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Zeyna is a reliable contact for:
    \begin{itemize}
        \item Rumours, overheard secrets, or missing persons.
        \item Shelter, gossip, or neutral ground.
        \item “Unauthorised” job offers passed through less official channels.
        \item Calling in favours owed by patrons who drank too much.
    \end{itemize}

    She’s tough, beloved, and untouchable—mostly because she knows where too many bodies are buried.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\textbf{+3 Read a Drunken Lie} \\
        \noindent\textbf{+2 Break Up a Fight with a Mug} \\
        \noindent\textbf{+2 Extract Confessions Over Tea} \\
        \noindent\textbf{+2 Recall Who Came In With Whom} \\
        \noindent\textbf{+2 Mix Drinks that Talk Back} \\
        \noindent\textbf{+2 Clean Up Blood without a Fuss}
    \subsubsection{Traits}
        \textbf{Three-Cup Truth} — Once per session, offer a drink that makes a target tell the truth (or say something more revealing than they meant to).\\
        \textbf{You’re Not the First} — Can reroll any defence against intimidation, seduction, or threats.
\end{paracol}

\vspace{.5\baselineskip}
\hrule
\vspace{.5\baselineskip}

\subsection{{\small Curator of Oddities and Old Names}\\ Ehvrem the Coilbound}
\label{npc:ehvrem-coilbound}

\emph{"Gold is one price. Memory is another. Tell me what spell you forgot, and I’ll tell you what it used to do."}
\vspace{.5\baselineskip}

\columnratio{0.375,0.375,0.25}
\begin{paracol}{3}
    \subsubsection*{Background:}
    Few know Ehvrem’s true nature—an ancient serpent of memory and time, bound by old magic into a human form with faint golden scales at the neck. Now he operates a modest tent of magical wares in the Salt Market, selling cursed trinkets, memory-bottles, and spells written on salted leather.

    His prices are fair but strange: a secret, a tear, a name you’ve never spoken aloud. Those who cheat him find they forget entire days… or wake up somewhere else entirely.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Ehvrem is a magical item vendor with narrative flair. He may:
    \begin{itemize}
        \item Sell rare spells, relics, or unstable artifacts.
        \item Require strange prices—emotional, spiritual, or symbolic.
        \item Offer cryptic guidance for spellcasters (especially Ashcraft or Bloodbinding).
        \item Warn of magical imbalances the players don’t yet understand.
    \end{itemize}

    He’s not malicious—but he is ancient, and his motives are not human.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\textbf{+3 Appraise Forgotten Magic} \\
        \noindent\textbf{+2 Bind Memory to Object} \\
        \noindent\textbf{+2 Speak with Sleeping Relics} \\
        \noindent\textbf{+2 Detect Magical Lies} \\
        \noindent\textbf{+2 Weave Truth into Fabric} \\
        \noindent\textbf{+2 Dispel a Curse by Name}
    \subsubsection{Traits}
        \textbf{What Is Forgotten Still Watches} — May reroll any magical knowledge check or recall a spell even the players don’t know yet.
\end{paracol}


\begin{multicols}{2}
