% !TeX root = ../../../wyrd.tex


\end{multicols}
\newpage
\section{Example PCs}

\begin{description}\raggedright
    \item[Kaelen Vire (page \pageref{pc:kaelen-vire})] --- A grim sellsword bearing a cursed blade and a deeper wound. Once a champion, now a haunted weapon-for-hire, Kaelen cuts through monsters and memory alike.

    \item[Idrani of the Ember Road (page \pageref{pc:idrani-ember})] --- A desert-born Ashcraft sorceress who weaves grief into flame. Idrani’s fire is both weapon and wound, burning brighter with every name she cannot forget.

    \item[Thariq the Viper-Handed (page \pageref{pc:thariq-viper})] --- A smiling thief raised in market alleys and snake pits. Thariq steals secrets, poisons rivals, and slips through shadows with venomous grace.

    \item[Father Mourn (page \pageref{pc:father-mourn})] --- An exiled priest of the Hollow Star, wandering the dunes with heretical prayers and a voice that twists the will of gods and mortals alike.

    \item[Vexa Flintspike (page \pageref{pc:vexa-flintspike})] --- A scarred mercenary who breaks relics for coin. Vexa solves magical problems with blunt force and alchemical charges—usually in that order.

    \item[Serenya of the Unbowed Veil (page \pageref{pc:serenya-veilborn})] --- A runaway princess turned desert survivor. Serenya hides nobility beneath sand-worn veils, her grace now a weapon, her exile a choice.
\end{description}

\newpage
\begin{WyrdCharacterSheet}
    {Kaelen Vire}
    {“I am the blade that never sleeps.”}
    \label{pc:kaelen-vire}

    Once a famed arena duelist, Kaelen Vire now wanders the edge of civilisation as a cursed sellsword. His blade—\textit{Whisperfang}—was earned in ritual combat, but its voice has never left him. Each foe he cuts, each night he survives, adds another whisper to the chorus. He doesn't seek glory. He seeks silence.

    \subsection{Background}
    Trained by the Bladed Crescent, Kaelen won his freedom by killing his master in sanctioned combat—then fled when the sword refused to let him rest. Now he fights for coin, travelling from city to ruin, answering to steel and nightmare alike.

    \subsection{Appearance}
    Broad-shouldered and quiet-eyed, Kaelen wears sand-scorched lamellar armour and a tattered dueling cloak. Whisperfang, curved and dark-bladed, hangs at his side. Its scabbard is wrapped in prayer cloth—and stained through.

    \subsection{Personality}
    Stoic, brutal, and unnervingly calm. Kaelen speaks little unless asked, but watches everything. He doesn’t relish violence—but he’s very, very good at it.

    \subsection{Connection to the World}
    Known in taverns and forts across the south. Feared by cultists, respected by caravan guards. Once hired by the Sapphire Concord, but left after a relic “spoke back.”

    \subsection{Goals}
    End the curse that binds his sword—and perhaps himself—to a cycle of violence.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Whisperfang, Cursed Blade] — +2 to Broadsword in melee; causes eerie whispers to rise when it draws blood.
        \item[Sand-Scorched Lamellar] — +2 to Survival (Desert) checks to resist sun, dust, or dehydration.
        \item[Prayer-Wrapped Fetish] — +2 to Will-based resistance rolls once per session (GM discretion).
    \end{GearBox}

    \begin{WyrdStatsBlock}[profile=img/characters/kaelen_vire]

        \begin{SkillsBox}
            \Expert & Broadsword \\
            \Skilled & Wrestling, Tactics, Survival (Desert) \\
            \Novice & Intimidation, Stealth, First Aid, Climbing, Hiking, Observation \\
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Whisperfang’s Curse] — Once per session, reroll a failed Broadsword attack. If successful, suffer 1 Fatigue.
            \item[No Openings Left] — +2 to Tactics when acting immediately after an enemy exposes themselves.
            \item[The Quiet Path] — +2 to Stealth when operating alone in dim light or ruinous terrain.
        \end{TraitsBox}



        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}



\newpage
\begin{WyrdCharacterSheet}
    {Idrani of the Ember Road}
    {“Grief is the kindling. I am the flame.”}
    \label{pc:idrani-ember}

    Idrani was born beneath the scalding skies of the southern caravan trails, raised by a dying cult of fire-keepers who taught her to sing the names of the dead into flame. When their shrine was destroyed, she walked alone—her grief becoming a weapon, her magic a mirror of all she lost. 

    She does not weep anymore. She burns.

    \subsection{Background}
    Idrani was once one of the Ember Acolytes, a dwindling sect that believed memory could be transmuted through fire. Her magic is Ashcraft—old, ritualistic, and tied to loss. The more she gives up, the stronger her flame becomes.

    \subsection{Appearance}
    Idrani wears cracked red silk robes over fire-scorched armour, her skin dusted with fine ash. Her left arm is tattooed with the names of her fallen kin—each one burned in by hand.

    \subsection{Personality}
    Controlled. Measured. Burning from within. Idrani is slow to trust but quick to act when lives are at risk. Her sorrow makes her strong, not soft.

    \subsection{Connection to the World}
    Wanderers, mourners, and broken cults know her name. She carries fire through forgotten places and offers light—if not always warmth.

    \subsection{Goals}
    To find the source of the dream-fire that speaks her name—and decide whether to embrace or destroy it.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Flamebrand Knife] — +2 to Ember Grasp or Ignite Object if the blade is drawn across skin or cloth.
        \item[Ember-Sigil Robes] — +2 to Stealth in dim light or smoke-filled areas.
        \item[Ash Pouch] — +2 to Occultism when consulting ashes, burnt bones, or fire remains.
    \end{GearBox}


    \begin{WyrdStatsBlock}[profile=img/characters/idrani_ember]

        \begin{SkillsBox}
            \Expert & Occultism \\
            \Skilled & Survival (Desert) \\
            \Novice & Fast-Talk, First Aid, Theology \\
        \end{SkillsBox}

        \begin{SkillsBox}[Spells]
            \Expert & Ember Grasp \\
            \Skilled & Ignite Object \\
            \Novice & Create Light, Breathe Ashes \\
        \end{SkillsBox}
        \ManaBox

        \begin{TraitsBox}
            \item[Ashcraft Adept] — Once per session, reduce the cost of a Fire spell by 1 Mana Point.
            \item[Burning Grief] — +2 to Occultism when invoking a spell using a personal loss or spoken name of the dead.
            \item[Endless Ember] — You can always light a fire, even in impossible conditions.
        \end{TraitsBox}


        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\begin{multicols}{2}
\section*{Idrani's Spells}
\begin{WyrdSpell}[Ashcraft]{Ember Grasp}
    \textit{Your hands glow with living embers, lashing out to burn or bind.}
    
    \begin{WyrdSpellBlock}
        \item[+1] Ignite a held object or scorch a touched enemy (1 stress or damage over time).
        \item[+2] Hurl embers in a cone; DL 2 Agility or take 1 Fatigue and be partially blinded.
        \item[+3] Wreath a target in flame-spirits. DL 3 Will or be bound by burning chains (immobile for 1 round).
    \end{WyrdSpellBlock}
\end{WyrdSpell}

\begin{WyrdSpell}[Elemental]{Ignite Object}
    \textit{Instantly spark flame in a flammable object. Used for kindling, sabotage, or swift destruction.}
    
    \begin{WyrdSpellBlock}
        \item[+1] Ignite a torch, candle, scroll, or other unattended object within reach.
        \item[+2] Ignite a small object at range (DL 2 to avoid if held). Burns immediately.
        \item[+3] Set multiple small objects ablaze or trigger a delayed ignition after a brief chant.
    \end{WyrdSpellBlock}
\end{WyrdSpell}

\begin{WyrdSpell}[Elemental]{Create Light}
    \textit{Summon a hovering orb or glow from ash, flame, or starlight. Ideal for navigation, warnings, or minor illusions.}
    
    \begin{WyrdSpellBlock}
        \item[+1] Produce a faint glow from your palm or a nearby object. Lasts several minutes.
        \item[+2] Create a floating orb of light that follows you or illuminates a small area.
        \item[+3] Shape the light into a beacon, symbol, or distraction. Causes confusion or awe in weak-minded creatures (DL 3 to resist).
    \end{WyrdSpellBlock}
\end{WyrdSpell}

\begin{WyrdSpell}[Ashcraft]{Breathe Ashes}
    \textit{You exhale a cloud of hot, choking ash to blind and disrupt enemies.}
    
    \begin{WyrdSpellBlock}
        \item[+1] Fill a small zone (1–2 targets) with swirling ash. Targets take a penalty to sight-based actions.
        \item[+2] Obscure a wider area. Targets must pass DL 2 or suffer coughing fits and mild disorientation.
        \item[+3] Create a choking storm of embers. Targets must pass DL 3 or suffer 1 Fatigue and become blinded for one round.
    \end{WyrdSpellBlock}
\end{WyrdSpell}

\end{multicols}


\newpage
\begin{WyrdCharacterSheet}
    {Thariq the Viper-Handed}
    {“Better a lie in the right ear than a knife in the wrong one.”}
    \label{pc:thariq-viper}

    Raised in the serpentine alleys of Hook Market, Thariq learned early that poison works better than steel, and a smile even better than both. Charming and quick-fingered, he thrives in shadows and crowded streets alike, slipping past guards, stealing secrets, and vanishing with a wink.

    \subsection{Background}
    Thariq grew up among snake-charmers, spice merchants, and cutthroats. Apprenticed to a wandering poison-brewer, he blended street charm with venom craft—and quickly outgrew both. Now he sells his services to anyone with coin, favouring work that keeps him moving, talking, and breathing.

    \subsection{Appearance}
    Graceful, wiry, and always moving. Wears flowing, loose desert garb with many hidden pockets. His fingers are stained with herbal oils and always smell faintly of cardamom and copper.

    \subsection{Personality}
    Affable, cocky, and calculating. Thariq loves stories, odds, and long games. He rarely stops smiling—even when he’s robbing you blind. Especially then.

    \subsection{Connection to the World}
    Known in every black market east of the Dustwind Flats. Has enemies in five city-states and lovers in seven. He never stays anywhere long enough for either to catch up.

    \subsection{Goals}
    To make enough coin to vanish on his own terms—and maybe pull one last impossible con.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Viper's Fang (Curved Blade)] — +2 to Knife when striking from stealth or after Fast-Talk success.
        \item[Smuggler’s Satchel] — +2 to Sleight of Hand or Lockpicking when tools are on hand.
        \item[Hook Market Poison Kit] — +2 to Poisons or Merchant checks when trading or testing alchemical vials.
    \end{GearBox}

    \begin{WyrdStatsBlock}[profile=img/characters/thariq_viper]

        \begin{SkillsBox}
            \Expert & Stealth \\
            \Skilled & Sleight of Hand, Fast-Talk, Poisons \\
            \Novice & Lockpicking, Pickpocket, Escape, Streetwise, Knife, Merchant \\
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Slippery as Smoke] — +2 to Escape when slipping restraints or escaping through a tight or crowded area.
            \item[Silver on the Tongue] — +2 to Fast-Talk when stalling, lying, or convincing someone of something unwise.
            \item[Snakework] — +2 to Poisons when applying toxins to blades, cups, or garments without being noticed.
        \end{TraitsBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage
\begin{WyrdCharacterSheet}
    {Father Mourn}
    {“The gods turned their faces. I kept walking.”}
    \label{pc:father-mourn}

    Once a battlefield chaplain of the Hollow Star, Father Mourn now wanders as a heretic, bearing a cracked holy symbol and a wrathful tongue. He calls down fire from forgotten gods and carves curses into the dust. He does not offer salvation. He offers warning.

    \subsection{Background}
    Mourn led troops in the divine wars of the western crusades, until he returned speaking new prayers no church would sanction. He’s since become part prophet, part executioner, part unwanted reminder of a faith that never answered back.

    \subsection{Appearance}
    Ragged cleric’s armour, blackened by soot and inscribed with blasphemous scripture. A relic-mace hangs from his belt, and his eyes gleam like embers beneath a cracked circlet.

    \subsection{Personality}
    Bitter, fearless, and cryptically kind. He believes faith is a weapon—and intends to use it.

    \subsection{Connection to the World}
    Whispers of “the war-priest who curses and heals with the same words” follow him through burned villages and buried temples. He sells prayers like spells—and leaves faster than the stories spread.

    \subsection{Goals}
    To unearth what was buried in the temple at Duskfall—and make the gods watch what comes next.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Star-Glass Staff] — +2 to Exorcism or Thaumatology when used during a full incantation.
        \item[Eclipse-Marked Relic] — +2 to Occultism when identifying cursed or celestial-afflicted objects.
        \item[Scorched Sermon Scroll] — +2 to Voice of the Hollow Star when read aloud during spirit confrontations.
    \end{GearBox}

    \begin{WyrdStatsBlock}[profile=img/characters/father_mourn]

        \begin{SkillsBox}
            \Expert & Exorcism \\
            \Skilled & Occultism, Thaumatology, Survival (Desert) \\
            \Novice & Intimidation, First Aid, Observation, Fast-Talk, Staff, Diagnosis \\
        \end{SkillsBox}

        \begin{SkillsBox}[Spells]
            \Skilled & Voice of the Hollow Star \\
        \end{SkillsBox}

        \ManaBox
        \DamageBox

        \begin{TraitsBox}
            \item[Blasphemous Rite] — +2 to Exorcism when performing rites in defiled or forbidden places.
            \item[The Gods Look Away] — Once per session, avoid divine backlash or spiritual harm entirely.
            \item[Covenant of Ashes] — +2 to Occultism when confronting or understanding undead or cursed spirits.
        \end{TraitsBox}



    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}


\begin{multicols}{2}
    \section*{Father Mourn's Spells}    
    \begin{WyrdSpell}[Divine]{Voice of the Hollow Star}
        \textit{Speak with the weight of forgotten gods. Your words carry the pressure of divine absence, driving spirits to silence or obedience.}
        
        \begin{WyrdSpellBlock}
            \item[+1] Your voice resonates unnaturally. Cause minor spiritual unease in one nearby creature—spirits may retreat, and mortals hesitate.
            \item[+2] Issue a direct command to a spirit, ghost, or cursed entity. DL 2 Will to resist compulsion or suffer 1 Fatigue.
            \item[+3] Utter a binding liturgy that suppresses a spirit’s powers for one scene. DL 3 Will to resist. If cast on a mortal, causes dread and silences speech or spellcasting.
        \end{WyrdSpellBlock}
    \end{WyrdSpell}
\end{multicols}



\newpage
\begin{WyrdCharacterSheet}
    {Vexa Flintspike}
    {“If it hums, glows, or begs—break it. Twice, if it talks.”}
    \label{pc:vexa-flintspike}

    Vexa Flintspike has no patience for curses, relics, or the fools who think they can control them. Once a siege sapper in the Ironhorn Wars, she now makes her living smashing ancient doors, disabling death traps, and blowing apart arcane machines too dangerous to study. If subtlety is required, hire someone else.

    \subsection{Background}
    Vexa grew up in the scorched mining camps of Korrad’s Spine, where you learn to work with blasting powder before you learn to read. After losing a hand to a collapsing glyph-wall, she forged her own prosthetic—and a new career. She’s been on every continent with a hammer in one hand and a bad idea in the other.

    \subsection{Appearance}
    Stocky and scarred, with soot-burned leathers and a prosthetic gauntlet made from bronze and bone. She carries a broad-bladed sword across her back and a crate of tools on her hip.

    \subsection{Personality}
    Crude, fearless, and practical. Believes most problems can be solved with enough force or the right lever. Doesn’t care much for theory—she cares what happens when you hit it.

    \subsection{Connection to the World}
    Known to black-market artificers, cursed ruins, and treasure-hunters too scared to open the final door. Everyone’s heard of a relic that went quiet after she visited.

    \subsection{Goals}
    Retire with both hands and most of her sanity. And maybe—just once—open a tomb and find something that doesn’t try to kill her.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Bronze Gauntlet (Prosthetic)] — +2 to Climbing or Broadsword when brute strength applies.
        \item[Satchel of Charges] — +2 to Armoury or First Aid when time is tight and consequences are loud.
        \item[Scrapblade Relic] — +2 to Broadsword when striking magical constructs, wards, or bound spirits.
    \end{GearBox}


    \begin{WyrdStatsBlock}[profile=img/characters/vexa_flintspike]

        \begin{SkillsBox}
            \Expert & Armoury (Melee Weapons) \\
            \Skilled & Broadsword, Occultism, Survival (Plains) \\
            \Novice & Climbing, Intimidation, First Aid, Diagnosis, Streetwise, Observation \\
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Break the Seal] — +2 to Armoury when disabling enchanted locks, seals, or magical traps.
            \item[Bones Know Better] — Once per session, declare you’ve seen something like this before and gain +2 to Occultism or Diagnosis.
            \item[Make Room or Else] — +2 to Intimidation when facing cultists, smugglers, or squabbling expedition teams.
        \end{TraitsBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}


\newpage
\begin{WyrdCharacterSheet}
    {Serenya of the Veilborn}
    {“The crown was never meant for me—so I stole a different fate.”}
    \label{pc:serenya-veilborn}

    Once promised to power, now sworn to freedom, Serenya of the Veilborn is a runaway noble who slipped from palace corridors into the wild edges of the world. Her bearing is graceful, her gaze defiant. She carries hidden truths, a stolen blade, and a name no longer spoken aloud.

    \subsection{Background}
    Born to the Moonpetal Dynasty and raised in the jeweled city of Zareth-Kai, Serenya was groomed for ceremonial duty and political alliance. But whispers of sacrifice, veiled rituals, and her own fate unraveled her loyalty. On the eve of her wedding to a foreign prince, she vanished—leaving behind a dagger in a silk pillow and the scent of desert wind. She now moves beneath many names, hunted by her past, yet chasing a future she shapes with her own hand.

    \subsection{Appearance}
    Veiled and adorned with desert silks, Serenya moves with court-trained poise and dancer’s precision. Gold-threaded sashes hide blades; kohl-rimmed eyes reveal little. Her beauty is tempered by resolve—and by the dirt of long travel on fine sandals.

    \subsection{Personality}
    Compassionate but calculating, Serenya is a natural diplomat who never forgets a slight. She speaks gently, moves gracefully, and strikes without hesitation when cornered. Though she rarely speaks of her heritage, it haunts every step she takes.

    \subsection{Connection to the World}
    Serenya’s name is still spoken—by bounty hunters, assassins, and spies of the Moonpetal Court. She knows secrets about royal rites and divine inheritance that others would kill to silence… or possess.

    \subsection{Goals}
    To escape the destiny others wrote for her—and to forge a legend of her own, not bound by blood, title, or temple.

    \vspace{0.5\baselineskip}
    \begin{GearBox}
        \item[Ceremonial Moonfang Blade] — +2 to Sword (Short); silvery blade concealable in dance silks or sashes.
        \item[Royal Signet, Hidden] — +2 to Fast-Talk or Diplomacy when revealed to assert lineage or command loyalty.
        \item[Veil of Many Names] — +2 to Disguise when assuming a false identity or hiding noble status.
    \end{GearBox}


    \begin{WyrdStatsBlock}[profile=img/characters/serenya_veilborn]

        \begin{SkillsBox}
            \Expert & Fast-Talk \\
            \Skilled & Sword (Short), Disguise \\
            \Novice & Acrobatics, Acting, Diplomacy, Escape, Knife, Observation, Stealth, Streetwise
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Silk and Steel] — +2 to Fast-Talk when using charm or status to manipulate someone in high society.
            \item[Born Beneath the Moonpetal Banner] — Once per session, declare a noble connection or past courtly lesson relevant to the current situation.
            \item[Grace Before All] — +2 to Acrobatics or Sword (Short) when fighting in close quarters or while performing a flourish.
        \end{TraitsBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}


\begin{multicols}{2}