\end{multicols}
\newpage
\section{Key NPCs}

In the following pages, you will find a selection of key NPCs designed to serve as recurring figures. Each character includes a brief description, a glimpse into their background, and a set of traits that can be used to enrich their presence, deepen interactions, and support the unfolding mystery in your game.

\begin{description}
    \item[Mr Alton Merriweather (page \pageref{npc:alton-merriweather})] --- The Chief Steward of the Grand Hall of Inquiry, Mr. Merriweather is a master of decorum and logistics. He oversees the estate’s day-to-day operations with clockwork precision, ensuring that investigators are well supplied and guests properly screened.

    \item[Inspector Quentin Hale (page \pageref{npc:inspector-hale})] --- A rising figure in the Metropolitan Police, Inspector Hale is known for his unwavering belief in procedure and a deep mistrust of private investigators. He often finds himself at odds with the Grand Society of Inquiry, viewing them as a disruptive influence on lawful investigation.
    
    \item[Kip “Knuckles” Mallory (page \pageref{npc:kip-mallory})] --- A streetwise information broker with a network of contacts throughout the city, Knuckles trades in secrets, half-truths, and debts too dirty for polite society. He is quick with a grin and quicker to vanish when the heat is on.

    \item[Dr Octavius Wren (page \pageref{npc:octavius-wren})] --- A brilliant but eccentric scientist, convinced that automata are gaining sentience. Publicly the leader of \emph{The Aetheric Liberty Assembly}, advocating for the rights of sentient machines, but secretly runs \emph{The Automata Liberation Army}—a radical group that seeks to free automata from oppression. He is a master of aetheric technology and has a knack for creating bizarre inventions.

\end{description}

\clearpage
    \subsection{{\small Chief Steward of the Grand Hall}\\ Mr Alton Merriweather}
    \label{npc:alton-merriweather}

        \emph{Unflappable, efficient, and eternally composed, Mr. Merriweather has served the Grand Society for over four decades—and he has never once been surprised.}
        \vspace{.5\baselineskip}
      
    \columnratio{0.375,0.375,0.25}
    \begin{paracol}{3}
        \subsubsection*{Background:}
        Mr Alton Merriweather has served as the chief butler and steward of the Grand Hall of Inquiry since the Society's early days. A master of decorum and logistics, he oversees the estate’s day-to-day operations with clockwork precision. Few know that he was once a field agent himself—though those who glimpse the faint scars beneath his cuffs might suspect a deeper past.
      
        Mr Merriweather maintains the perfect balance of discretion and authority. He ensures that investigators are well supplied, guests properly screened, and that no detail in the Grand Hall ever falls into disorder. While he speaks in clipped, courteous tones, there is steel behind his gaze and loyalty in every action.
      
        \switchcolumn
        \subsubsection*{Using in Play:}
        Mr Merriweather is an anchor NPC—reliable, ever-present, and a point of continuity between investigations. He can:
        \begin{itemize}
          \item Deliver mission briefings or dossiers from the Society’s analysts.
          \item Provide subtle guidance or nudge players toward overlooked details.
          \item Secure equipment, lodgings, or discreet transport.
          \item Offer cryptic remarks hinting at the Society’s deeper secrets.
        \end{itemize}
        He is not meant to overshadow the players, but rather to support them—like the butler in a mystery novel who knows more than he lets on. In times of need, he may reveal surprising resourcefulness, especially if the Grand Hall is ever under threat.
      
        \switchcolumn      
        \subsubsection{Skills}
            \noindent\Expert: Etiquette \\
            \noindent\Skilled: Insight, Logistics \\
            \noindent\Novice: Stealth, Medicine, Presence \\
        \subsubsection{Traits}
          \textbf{Unseen, Unshaken} — Once per session, appear at just the right moment—regardless of obstacles or distance.
      
    \end{paracol}
    \vspace{.5\baselineskip}
    \hrule
    \vspace{.5\baselineskip}

    \subsection{{\small By-the-Book Investigator}\\ Inspector Quentin Hale}
    \label{npc:inspector-hale}
    
    \emph{A stern and rising figure in the Metropolitan Police, Inspector Hale is known for his unwavering belief in procedure and a deep mistrust of private investigators.}
    \vspace{.5\baselineskip}
    
    \columnratio{0.375,0.375,0.25}
    \begin{paracol}{3}
        \subsubsection*{Background:}
        Inspector Quentin Hale is a career man with aspirations of high office. Intelligent, meticulous, and unyielding, he considers the Grand Society of Inquiry a disruptive influence on lawful investigation. While not antagonistic out of malice, his dedication to procedure and political advancement frequently puts him at odds with the Society’s methods. Despite this, he may occasionally seek their help when a case falls outside conventional explanation—grudgingly, of course.
        
        \switchcolumn
        \subsubsection*{Using in Play:}
        Inspector Hale works best as a recurring foil or rival—an NPC who applies pressure, raises stakes, and reminds players that their investigations exist within a broader system of law and politics. He may:
        \begin{itemize}
          \item Attempt to take over a case or block access to key evidence.
          \item Arrest a scapegoat if the players delay or antagonize him.
          \item Undermine the Grand Society’s reputation with the authorities.
          \item Call on the players in private when a case becomes “irregular.”
        \end{itemize}
        Use Hale to inject conflict, force clever diplomacy, or complicate scenes where the players operate in the open.
        
        \switchcolumn      
        \subsubsection{Skills}
            \noindent\Expert: Reasoning \\
            \noindent\Skilled: Discipline, Command \\
            \noindent\Novice: Awareness, Presence, Investigation \\
        \subsubsection{Traits}
            \textbf{Procedure is Power} — Gains a bonus when solving problems by following official protocols to the letter.\\
            \noindent\textbf{Authoritative Glare} — Can reroll when using rank or command presence to compel obedience.\\
    \end{paracol}

    \clearpage
    \subsection{{\small Whisper Broker}\\ Kip “Knuckles” Mallory}
    \label{npc:kip-mallory}
    
    \emph{Quick with a grin and quicker to vanish, Knuckles trades in secrets, half-truths, and debts too dirty for polite society.}
    \vspace{.5\baselineskip}
    
    \columnratio{0.375,0.375,0.25}
    \begin{paracol}{3}
        \subsubsection*{Background:}
        Kip Mallory, known on the streets as “Knuckles,” is an ex-pickpocket turned information broker. With a network of urchins, cabbies, and dockhands, he collects the underbelly’s whispers about crimes, scandals, and disappearances. Though rough around the edges, he is clever, pragmatic, and loyal to those who pay fairly and ask the right way.
        
        \switchcolumn
        \subsubsection*{Using in Play:}
        Knuckles is ideal for providing street-level intel—revealing cryptic leads and information the authorities overlook. He can:
        \begin{itemize}
          \item Drop hints about recent events or persons of interest.
          \item Offer minor favors in exchange for coin or a promise of future assistance.
          \item Connect players with the criminal underworld or serve as a bridge to dubious allies.
          \item Betray the party if their reputation becomes too dangerous.
        \end{itemize}
        Use him to add local color, steer investigations, and introduce tension from the shadows.
        
        \switchcolumn      
        \subsubsection{Skills}
            \noindent\Expert: Streetwise \\
            \noindent\Skilled: Deception, Awareness \\
            \noindent\Novice: Stealth, Presence, Mobility \\
        \subsubsection{Traits}
            \textbf{Too Quick to Catch} — Can reroll when evading capture or disappearing into a crowd.\\
            \noindent\textbf{Favour for a Favour} — Once per session, declare a helpful contact or resource—but you’ll owe Knuckles for it later.
    \end{paracol}
    \vspace{.5\baselineskip}
    \hrule
    \vspace{.5\baselineskip}

    \subsection{{\small Grand Artificer of the Aetheric Liberty Assembly}\\ Dr Octavius Wren}
\label{npc:octavius-wren}

    \emph{Visionary, rebel, and scholar of the forbidden spark. Dr Wren dreams not of progress, but of liberation through invention.}
    \vspace{.5\baselineskip}
  
    \columnratio{0.375,0.375,0.25}
    \begin{paracol}{3}
    \subsubsection*{Background:}
    Once a lauded professor at the Royal College of Natural Philosophy, Dr Octavius Wren vanished from public life after his controversial treatises on sentient automata and free energy were suppressed by the Crown. Years later, he re-emerged as the charismatic leader of the Aetheric Liberty Assembly—a coalition of inventors, exiles, and rogue thinkers who believe true freedom lies in decentralised aetheric technology.

    Secretly, he has been building the Automata Liberation Army from the more radical members of the Assembly. He believes that automata are gaining sentience and that they deserve the same rights as humans, and he and the Liberation Army are willing to go to any lengths to achieve this goal.

    \switchcolumn
    \subsubsection*{Using in Play:}
    Dr Wren can serve as:
    \begin{itemize}
      \item A philosophical foil to players who favour order over innovation.
      \item A source of illicit information, rare devices, or urgent warnings.
      \item A wildcard ally when a common threat emerges—though always on his own terms.
      \item The architect of a grand aetheric event that spirals out of control.
    \end{itemize}
    Though he speaks of liberty, Wren may sacrifice much in the name of progress—including people.

    Wren sees the Grand Society not as enemies, but as blind custodians of a decaying system. His speeches blend poetic fervour with mechanical insight, and his presence inspires fierce loyalty among his followers. Though soft-spoken and refined, there’s an unmistakable intensity in his eyes—a man who has glimpsed a world remade.

    \switchcolumn
    \subsubsection{Skills}
        \noindent\Expert: Engineering \\
        \noindent\Skilled: Rhetoric, Lore \\
        \noindent\Novice: Deception, Insight, Resources \\
    \subsubsection{Traits}
        \textbf{Voice of the Future} — When addressing a crowd or debating ideology, Wren gains advantage and can shift the mood of a scene. \\

    \end{paracol}
    % \vspace{.5\baselineskip}
    % \hrule
    % \vspace{.5\baselineskip}