\newpage
\section{Example PCs}

\begin{description}\raggedright
    \item[Dr Alistair Hargrave (page \pageref{pc:alistair-hargrave})] --- A haunted physician turned occult researcher. Once a man of science, now a seeker of forbidden knowledge, Hargrave investigates unnatural afflictions with steady hands and a fractured soul.

    \item[Eleanor "Ellie" Fairchild (page \pageref{pc:eleanor-fairchild})] --- A fearless investigative journalist with a sharp tongue and sharper instincts. Known for exposing high-society corruption, Ellie uses charm and determination to uncover the truths others want buried.

    \item[Jonathan "Jack" Blackwood (page \pageref{pc:jack-blackwood})] --- A disgraced noble turned private investigator. Jack moves between London's underbelly and drawing rooms with equal ease, wielding secrets like daggers as he hunts for redemption—or revenge.

    \item[Margaret "Maggie" Holloway (page \pageref{pc:maggie-holloway})] --- A brilliant and manipulative criminal psychologist. Maggie sees through people with terrifying ease, using intellect, charm, and psychological insight to bend others to her will.

    \item[Genevieve "Ginny" Harcourt (page \pageref{pc:ginny-harcourt})] --- A rogue intelligence agent and steampunk spy. Armed with gadgets, disguises, and a mind for intrigue, Ginny operates outside the law to expose the powerful and vanish before the dust settles.
\end{description}
    
\newpage

\begin{WyrdCharacterSheet}
    {Dr Alistair Hargrave} 
    {“Some afflictions cannot be cured, only contained.”}
    \label{pc:alistair-hargrave}

    Once a man of science and reason, Dr Alistair Hargrave now treads the blurred line between medicine and the arcane. What began as a pursuit of healing has become a descent into hidden truths that defy biology—and sanity. Calm, precise, and increasingly haunted, Hargrave seeks to understand what lies beyond the edges of knowledge… even if it consumes him.

    \subsection{Background}
    Hargrave trained as a physician and researcher, once celebrated for his cutting-edge theories. But patients began whispering of dreams, disappearances, and impossible recoveries. A single case—a child who spoke in tongues not found in any human language—shattered his trust in reason. Since then, he’s walked a solitary path, one paved with questions best left unasked.

    \subsection{Appearance}
    Neatly dressed in a weathered frock coat, spectacles perched on a tired face. His hands are steady, his expression detached. A stethoscope hangs beside a worn leather satchel filled with instruments for both surgery and séance.

    \subsection{Personality}
    Brilliant, methodical, and burdened by knowledge. Hargrave is driven to discover, even when discovery cuts deep. He keeps his emotions buried beneath a surgeon’s calm—but nightmares press ever closer to the surface.

    \subsection{Connection to the Casebook}
    His research into “unusual afflictions” brought him into contact with the Grand Society of Inquiry. Though not a formal member, he is often consulted when a case involves biology gone wrong—or something pretending to be biology.

    \subsection{Goals}
    To identify, isolate, and if possible, contain the unnatural. Whether his goal is to save humanity or himself remains unclear—even to him.

    \begin{WyrdStatsBlock}[profile=img/characters/alistair_hargrave]

        \begin{SkillsBox}
            \Expert & Lore \\
            \Skilled & Investigate, Will \\
            \Novice & Rapport, Crafts, Empathy
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Scientific Method] — +2 to Investigate when analysing evidence, conducting experiments, or applying rational deduction.
            \item[Occult Intuition] — Once per session, substitute Lore for any other skill when interpreting the supernatural.
            \item[Steady Hands, Sharp Mind] — +2 to Crafts when performing delicate work or acting under extreme pressure.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Electro-Aetheric Analyzer] — +2 to Lore when detecting or analysing supernatural phenomena; extended use may cause hallucinations.
            \item[Pocket Revolver] — +2 to Shoot in close-quarters conflict; discreet and reliable.
            \item[Notebook of the Unknown] — +2 to Lore when researching entities or events, though prolonged study risks psychological strain.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage

\begin{WyrdCharacterSheet}
    {Eleanor "Ellie" Fairchild} 
    {“Fear won't stop me. Lies won't fool me. Power won't silence me.”}
    \label{pc:eleanor-fairchild}

    Eleanor "Ellie" Fairchild is an investigative journalist with a reputation for uncovering the truth—especially the kind others would prefer stayed buried. Armed with charm, wit, and a steel resolve, Ellie chases leads through high society soirées and back-alley whispers alike. She’s not just looking for a story—she’s looking for justice.

    \subsection{Background}
    Ellie made her name exposing corruption in Parliament and industry alike. Her column in the underground press made waves until it was abruptly shut down after a scandal she never got to print. She suspects powerful hands buried the truth, and now she works freelance, answering only to herself—and the stories that need telling.

    \subsection{Appearance}
    Stylish but practical—blouses with hidden pockets, corsets that conceal notebooks, and gloves perfect for opening locked doors. Her sharp green eyes miss nothing, and her confident posture keeps her one step ahead of suspicion.

    \subsection{Personality}
    Fearless, driven, and cunning. Ellie knows when to press for answers and when to play coy. She believes that stories can save lives—or ruin them—and she’s not afraid to take that gamble. Her charm is real, but so is her steel.

    \subsection{Connection to the Casebook}
    A recent letter warned her off a lead she hadn’t yet begun to chase—about strange disappearances tied to the Society of Inquiry. Now she’s chasing the sender as much as the story.

    \subsection{Goals}
    Expose the forces manipulating the truth. Whether it’s a secret society or something older, she’ll dig until she hits the nerve—and print it, no matter the cost.

    \begin{WyrdStatsBlock}[profile=img/characters/eleanor_fairchild]

        \begin{SkillsBox}
            \Expert & Investigate \\
            \Skilled & Rapport, Empathy \\
            \Novice & Contacts, Notice, Will, Stealth
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Follow the Lead] — +2 to Investigate when pursuing a major story or unraveling a cover-up.
            \item[Silver-Tongued Reporter] — Once per session, substitute Rapport for Deceive when gathering information.
            \item[Ink Over Iron] — +2 to Will when resisting intimidation, coercion, or supernatural manipulation.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Press Credentials] — +2 to Rapport when convincing someone to talk on the record.
            \item[Lockpicking Kit] — +2 to Stealth when breaking into offices or restricted archives.
            \item[Hidden Notes and Records] — +2 to Investigate when reviewing past leads or building a case.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage

\begin{WyrdCharacterSheet}
    {Jonathan "Jack" Blackwood} 
    {“Justice? That’s for men with clean hands. I settle for truth.”}
    \label{pc:jack-blackwood}

    Once a privileged nobleman, now a disgraced investigator, Jonathan "Jack" Blackwood navigates the shadows of the same society that cast him out. Suave, jaded, and sharper than ever, he deals in secrets—especially the kind that destroy reputations. Though the city turned its back on him, Jack learned to thrive in its alleys, clubs, and drawing rooms alike.

    \subsection{Background}
    Born into aristocracy, Jack lived a life of comfort until scandal drove him from polite society. The details remain elusive, but whispers of cover-ups and betrayal follow him still. He now works as a private investigator, using his knowledge of the elite to expose their sins—and perhaps, someday, redeem his own.

    \subsection{Appearance}
    Trim and refined, but with a weariness in his eyes that betrays years of hard truth. Always impeccably dressed, though his coat bears the wear of back alleys and long nights. He moves with confidence, but not the kind that comes from wealth—it’s the confidence of survival.

    \subsection{Personality}
    Witty and worldly, Jack is equal parts cynic and romantic. He sees the rot beneath the city’s glittering mask but keeps a code of honour all the same. His charm is effortless, but his past is heavy, and it never stays buried for long.

    \subsection{Connection to the Casebook}
    The Society sometimes turns to Jack when an investigation involves the upper crust. His ability to blend into ballrooms or brothels alike makes him a valuable—if reluctant—asset.

    \subsection{Goals}
    To uncover the truth behind his exile and hold the guilty accountable—if not in court, then in kind. And if that truth damns him too? So be it.

    \begin{WyrdStatsBlock}[profile=img/characters/jack_blackwood]

        \begin{SkillsBox}
            \Expert & Investigate \\
            \Skilled & Rapport, Notice \\
            \Novice & Deceive, Stealth, Contacts
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Aristocratic Charm] — +2 to Rapport when dealing with upper-class individuals or navigating elite social circles.
            \item[A Shadow Among Shadows] — Once per session, use Stealth to escape pursuit in crowds or dimly lit environments.
            \item[Secrets Kept, Secrets Sold] — +2 to Contacts when dealing with informants or acquiring blackmail material.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Forged Identity Papers] — +2 to Deceive when infiltrating parties, clubs, or restricted events.
            \item[Hidden Dagger] — +2 to Stealth when concealing a weapon or retrieving it undetected.
            \item[The Ledger of Secrets] — +2 to Investigate when researching aristocratic corruption or tracing hidden transactions.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage

\begin{WyrdCharacterSheet}
    {Margaret "Maggie" Holloway} 
    {“Every mind has a door. I simply know how to open them.”}
    \label{pc:maggie-holloway}

    \raggedright
    Maggie Holloway is a master manipulator wrapped in charm and poise. A criminal psychologist of rare brilliance, she dissects people the way others read poetry — elegantly, and without mercy. Whether uncovering a motive or\\ planting a seed of doubt, she always knows what to say — and when silence will say more.

    \subsection{Background}
    Maggie rose to prominence as a forensic psychologist, consulting for both the courts and the clandestine. Her insight made her enemies, her confidence made her dangerous. Officially, she "stepped away" from academia. Unofficially, she's still invited to solve the kinds of puzzles most professionals refuse to touch.

    \subsection{Appearance}
    Always impeccably dressed in tailored black, Maggie's presence is commanding without being loud. Her voice is soft but sharp, her eyes calm but invasive. She speaks like she already knows what you're about to say.

    \subsection{Personality}
    Intelligent, composed, and subtly dangerous. She prefers manipulation to confrontation and keeps her emotions in a locked box. While her methods are unsettling, her results are undeniable.

    \subsection{Connection to the Casebook}
    Maggie consults for the Grand Society when cases require psychological nuance—or when suspects are best broken with words rather than force. She rarely seeks out mysteries, but they often find her.

    \subsection{Goals}
    To study the darker corners of the human mind—and use that knowledge as both scalpel and sword. Whether her motives are pure is a matter of perspective.

    \begin{WyrdStatsBlock}[profile=img/characters/maggie_holloway]

        \begin{SkillsBox}
            \Expert & Empathy \\
            \Skilled & Rapport, Investigate \\
            \Novice & Deceive, Will, Contacts
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Mind Games] — +2 to Empathy when analysing emotional states or hidden motives.
            \item[Persuasive Whisper] — Once per session, use Empathy in place of Rapport to subtly influence a target.
            \item[Puppet Master] — +2 to Deceive when manipulating someone into action against their interest.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Psychological Dossier] — +2 to Investigate when reviewing notes or case files on a subject’s behaviour.
            \item[Silver Locket] — +2 to Rapport when forging emotional connections through shared memories or vulnerability.
            \item[A Hidden Letter] — +2 to Contacts when calling in favours from influential acquaintances.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage

\begin{WyrdCharacterSheet}
    {Genevieve "Ginny" Harcourt} 
    {“Secrets are just another kind of weapon.”}
    \label{pc:ginny-harcourt}

    Once a decorated agent of the Crown, Ginny Harcourt now moves through the shadows of the Empire, answerable to no one. Betrayed and disavowed, she has turned her considerable talents toward subterfuge, sabotage, and secrets. Her enemies never see her coming—only the aftermath.

    \subsection{Background}
    A brilliant operative with a reputation for infiltration and extraction, Ginny was betrayed by her handlers and left for dead after uncovering secrets too dangerous for the Empire to admit. She now works as a rogue agent, unravelling conspiracies with a mixture of charm, cunning, and clever engineering.

    \subsection{Appearance}
    Always dressed for movement, with hidden tools stitched into every layer. Her presence shifts to suit her role—noblewoman, servant, smuggler, spy. Her eyes are sharp, her smile misleading, and her pockets full of tricks.

    \subsection{Personality}
    Coldly efficient, but never without style. Ginny calculates three moves ahead and keeps her heart locked behind iron discipline. Trust is rare. Precision is everything.

    \subsection{Connection to the Casebook}
    The Grand Society occasionally requires the skills of someone who doesn’t officially exist. Ginny helps with the cases no one else is allowed to know about.

    \subsection{Goals}
    To uncover the truth behind her betrayal and dismantle the power structures that let it happen—one secret at a time.

    \begin{WyrdStatsBlock}[profile=img/characters/ginny_harcourt]

        \begin{SkillsBox}
            \Expert & Deceive \\
            \Skilled & Stealth, Investigate \\
            \Novice & Burglary, Contacts, Crafts
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Master of Disguise] — +2 to Deceive when impersonating others or assuming a false identity.
            \item[Escape Artist] — Once per session, declare an escape plan was already prepared—automatically succeed at leaving danger behind.
            \item[Tinker’s Friend] — Use Crafts instead of Burglary when bypassing security systems or traps.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Hidden Blade] — +2 to Fight when striking from stealth or ambush.
            \item[Encrypted Communicator] — +2 to Contacts when sending or receiving secure messages.
            \item[Grappling Hook Gauntlet] — +2 to Athletics when climbing or fleeing through vertical terrain.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}
