% !TeX root = ../../../wyrd.tex

\end{multicols}
\newpage
\section{Example PCs}

\begin{description}\raggedright
    \item[Jolene “Jojo” Pickens (page \pageref{pc:jolene-pickens})] --- A sharp-tongued former pageant queen with fire magic in her veins and a grudge against glamour. Jojo has opinions, heels for days, and zero patience for magical nonsense—or anyone who underestimates her.

    \item[Clem “Fix-It” Rayburn (page \pageref{pc:clem-rayburn})] --- A grease-streaked handyman with a possumshine flask and a toolkit full of cursed wrenches. Clem knows every weird leak and supernatural short circuit in the park, and fixes them with duct tape, cussing, and a surprising amount of love.

    \item[Marlow Teague (page \pageref{pc:marlow-teague})] --- A fae-blood drifter with windblown hair, cryptic warnings, and a heart full of haunted poetry. Marlow hears things others don’t, sees what shouldn’t be seen, and always knows when a storm is coming.

    \item[Teddy “Rabbit Hole” Muldoon (page \pageref{pc:teddy-muldoon})] --- A conspiracy theorist turned magical investigator with a bean-based divination system and too many radios. Teddy is Dusty Pines’ unofficial surveillance department and the first to shout “I told you so!” when things go weird.

    \item[Linda Mae Bellweather (page \pageref{pc:linda-mae})] --- A no-nonsense retiree with a bottomless tote bag and iron willpower. Linda Mae doesn’t believe in magic—and somehow, that makes her immune to half of it. She bakes banana bread and stares down poltergeists like they’re noisy neighbours.
\end{description}
    
\newpage
\begin{WyrdCharacterSheet}
    {Jolene “Jojo” Pickens}
    {“Ain’t no ghost, gremlin, or glamoured elf tougher than me before coffee.”}
    \label{pc:jolene-pickens}

    A retired rodeo queen turned supernatural troubleshooter, Jojo came to Dusty Pines looking for peace and wound up as the unofficial sheriff, monster-wrangler, and party planner. With her charm, grit, and glitter-loaded shotgun, she handles magical nonsense like it’s just another day in the arena. Trouble doesn’t scare her—boredom does.

    \subsection{Background}
    Jojo toured the paranormal rodeo circuit for most of her youth, performing death-defying stunts and banishing spirits from haunted barns. After a particularly disastrous exorcism involving possessed cattle and one flaming clown car, she packed up her enchanted lasso and settled down in Dusty Pines. She claims it was for “quiet nights.” No one believes her.

    \subsection{Appearance}
    Denim jacket embroidered with protective sigils, bedazzled pink cowboy boots, and a shotgun holster that sparkles with suspicious enchantments. Her hat’s got more wards than most grimoires. Always smells faintly of barbecue and ozone.

    \subsection{Personality}
    Loud, loyal, and completely unbothered by weirdness. She treats eldritch horrors like stubborn bulls—shout loud, stand your ground, and don’t let ’em see you sweat. She’s got a soft spot for underdogs and a short fuse for anyone threatening her home.

    \subsection{Connection to Dusty Pines}
    Moved in “temporarily” three years ago and somehow ended up organizing the anniversary potluck and exorcising three cursed trailers. Bobby considers her his emergency contact (and possibly his emotional support cowgirl).

    \subsection{Goals}
    To keep Dusty Pines safe, get the barbecue working again, and finally beat Edna in the “Best Chili, Worst Curse” cook-off.

    \begin{WyrdStatsBlock}[profile=img/characters/jolene_picken]

        \begin{SkillsBox}
            \Expert & Grit \\
            \Skilled & Charm, Shoot \\
            \Novice & Drive, Athletics, Exorcism
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Glitter and Gumption] — +2 to Charm or Grit when solving a problem in a loud, flamboyant, or over-the-top way.
            \item[Ghost Wrangler] — Once per session, trap a spirit or minor supernatural entity using improvised tools (glitter, duct tape, lasso, etc.).
            \item[Can't Keep a Good Cowgirl Down] — The first time you're Taken Out each session, remain conscious with 1 Wound and a dramatic comeback line.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Glitterbuck Shotgun] — +2 to Shoot when targeting supernatural creatures; may blind bystanders if used recklessly.
            \item[Enchanted Lasso] — +2 to Athletics or Exorcism when restraining entities or yanking items from dangerous places.
            \item[“Emergency Coffee” Flask] — +2 to Grit once per session; restores 1 Fatigue box if consumed with dramatic flair.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage
\begin{WyrdCharacterSheet}
    {Clem “Fix-It” Rayburn}
    {“If duct tape don’t work, it wasn’t meant to be fixed.”}
    \label{pc:clem-rayburn}

    Born in a shack, raised in a trailer, and possibly part possum (spiritually speaking), Clem is the closest thing Dusty Pines has to a maintenance man—and a walking supernatural hazard sign. He’s patched up every roof in the park with beer cans and hex-resistant tar, and once accidentally banished a poltergeist with WD-40 and a slap.

    \subsection{Background}
    Clem never left the park. His mama ran a bootleg moonshine operation in Lot 4, and his daddy vanished into a pocket dimension after trying to build a still with magical scrap. Clem grew up chewing copper wire and fixing things that oughta stay broken. He knows every leak, creak, and cursed corner of Dusty Pines.

    \subsection{Appearance}
    Overalls, no shirt. Grease-stained ball cap that says “I Void Warranties.” Always carrying a toolkit, a switchblade screwdriver, and at least three rats named after ex-girlfriends. Smells faintly of ozone and motor oil.

    \subsection{Personality}
    Cheerfully unbothered by danger, enthusiastic about weird problems, and dangerously curious. Clem is the kind of guy who pokes the magical anomaly with a stick—and then tries to date it. He means well, and he fixes things… eventually.

    \subsection{Connection to Dusty Pines}
    He’s the guy everyone calls when a trailer starts levitating, the toilet growls, or the fridge dimensionally folds. He’s never been paid on time, and that’s never stopped him.

    \subsection{Goals}
    To keep the park held together with grit, guts, and Gorilla Glue—and maybe finally get that date with Edna. Or the sentient toaster. He’s open-minded.

    \begin{WyrdStatsBlock}[profile=img/characters/clem_rayburn]

        \begin{SkillsBox}
            \Expert & Crafts \\
            \Skilled & Notice, Grit \\
            \Novice & Stealth, Lore, Burglary
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[It Ain’t Pretty, But It Works] — +2 to Crafts when improvising a solution with junk, trash, or questionable materials.
            \item[Hex Magnet] — Once per session, redirect a magical mishap or side effect onto yourself (intentionally or not) and turn it into a temporary advantage.
            \item[The Park Runs on Duct Tape] — Once per session, instantly repair or disable a mechanical or magical device—though there’s a 50/50 chance it explodes later.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Multiversal Monkey Wrench] — +2 to Crafts when dealing with magical constructs, cursed engines, or sentient plumbing.
            \item[Possumshine Flask] — Grants +2 to Grit or causes hallucinations (roll a die). Clem drinks it regardless.
            \item[Cursed Toolkit] — Add +2 to any jury-rigged solution, but every success makes nearby lights flicker ominously.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}


\newpage
\begin{WyrdCharacterSheet}
    {Marlow Teague}
    {“I didn’t mean to stay. But the winds here... they whisper like home.”}
    \label{pc:marlow-teague}

    A wandering fae-blood with a suitcase full of secrets and a map that doesn’t show roads, Marlow arrived at Dusty Pines during a thunderstorm and never left. They make charms from bottle caps, predict the weather with bird bones, and speak five languages—including two only remembered by rivers.

    \subsection{Background}
    Born somewhere between the mortal world and the softer places just beyond it, Marlow was raised by an aunt who told fortunes from dandelion seeds and warned them never to eat moonlight. They’ve spent most of their life drifting from enchanted roadside motels to haunted bus stops, always a little out of step with the world. Dusty Pines is the first place that’s ever let them rest.

    \subsection{Appearance}
    Tall, with mismatched eyes and hair that always looks windblown. They wear layered shawls, patched coats, and boots held together with knotted string and stubbornness. Often seen scribbling in a journal or feeding something unseen from their pocket.

    \subsection{Personality}
    Quiet, cryptic, and surprisingly kind. Marlow speaks in metaphors more often than not and tends to stare into the middle distance when things get weird. They’re terrible with technology but excellent with curses, riddles, and haunted vending machines.

    \subsection{Connection to Dusty Pines}
    Took over a half-burned trailer on the edge of the park and never bothered to explain where they came from. Everyone assumes they’re magical, or possibly cursed. Either way, they’re good company and always bring something weird to potlucks.

    \subsection{Goals}
    To stay hidden from their past, protect the fragile balance between worlds, and find a good recipe for cornbread that works during eclipses.

    \begin{WyrdStatsBlock}[profile=img/characters/marlow_teague]

        \begin{SkillsBox}
            \Expert & Lore \\
            \Skilled & Empathy, Stealth \\
            \Novice & Notice, Charm, Will
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Born Beneath a Stranger Star] — +2 to Lore or Empathy when interacting with fae, spirits, or otherworldly beings.
            \item[The Wind Remembers] — Once per session, ask the GM for a cryptic clue, warning, or insight—delivered through weather, birds, or the park’s weird radio.
            \item[Unnerving Calm] — +2 to Will when resisting magical influences, fear, or glamour. You can pass this bonus to another with a single look.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Fae-Crafted Compass] — +2 to Lore or Notice when tracking magical energy or sensing veil-thin places.
            \item[Patchwork Cloak] — Grants +2 to Stealth in overgrown, liminal, or dark places; smells faintly of lavender and secrets.
            \item[Charms and Oddments] — Once per session, pull a small, oddly useful magical trinket from your satchel.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\newpage
\begin{WyrdCharacterSheet}
    {Teddy “Rabbit Hole” Muldoon}
    {“You can’t spell ‘truth’ without ‘trailer park’... well, not directly, but you get it.”}
    \label{pc:teddy-muldoon}

    Teddy has a whiteboard covered in string, a drawer full of labelled beans (they’re important), and a secret stash of cursed bingo cards. He believes Dusty Pines is a nexus of magical conspiracies—and the more time you spend here, the harder it is to argue with him.

    \subsection{Background}
    Once a local radio host running a show on “unsolved supernatural incidents,” Teddy was fired after broadcasting a three-hour exposé on gremlins living in microwaves. He took his savings, bought a used trailer, and dedicated himself full-time to uncovering the truth about Dusty Pines, the fae, and “Project FLAMINGO.”

    \subsection{Appearance}
    Disheveled hoodie, camo cargo shorts, and at least two pairs of sunglasses (worn at once). Often seen hauling an old tape recorder, a pocket scanner, and a clipboard full of deeply concerning diagrams.

    \subsection{Personality}
    Paranoid but affable, endlessly enthusiastic, and genuinely convinced he’s saving the world. Teddy gets distracted easily, makes wild leaps of logic, and is surprisingly effective when it comes to uncovering actual secrets.

    \subsection{Connection to Dusty Pines}
    He lives in Lot 7B and believes the entire trailer park sits on a “magical soft spot.” The fae, the government, and Edna are all watching. He’s here to document everything and protect his neighbours—whether they want him to or not.

    \subsection{Goals}
    To expose the truth, earn the respect of his fellow residents, and finally connect the dots between Tito the Chupacabra and the rogue port-a-potty.

    \begin{WyrdStatsBlock}[profile=img/characters/teddy_muldoon]

        \begin{SkillsBox}
            \Expert & Notice \\
            \Skilled & Lore, Provoke \\
            \Novice & Burglary, Will, Stealth
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[Red String Logic] — +2 to Lore or Notice when connecting unrelated clues to form a theory. Bonus applies even if the theory is completely unhinged.
            \item[Trust No One (Except Maybe Edna)] — +2 to Will when resisting manipulation, illusions, or magical persuasion.
            \item[“I Knew It!”] — Once per session, declare you’ve “already been watching” a situation and retroactively appear with useful intel or evidence.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Modified Radio Scanner] — +2 to Notice when eavesdropping on magical frequencies or detecting hidden enchantments.
            \item[Conspiracy Notebook] — +2 to Lore once per scene when proposing a theory or making a wild deduction.
            \item[Beans of Revelation] — Once per session, roll beans like dice to ask the GM a yes/no question (the answer is never straightforward).
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}


\newpage
\begin{WyrdCharacterSheet}
    {Linda Mae Bellweather}
    {“I don’t believe in magic. Never have. Never will. Now hand me that gnome, it’s chewing on my begonias.”}
    \label{pc:linda-mae}

    Linda Mae is the most aggressively normal woman in Dusty Pines. She bakes banana bread, enters every park raffle, and refuses to acknowledge the chupacabra that keeps stealing her slippers. She also hasn’t aged in ten years, walked through at least three hex zones unharmed, and once told a poltergeist to “hush up” until it listened.

    \subsection{Background}
    Retired from a long career in municipal tax enforcement, Linda Mae came to Dusty Pines for peace and quiet. What she got was cursed plumbing, time-travelling garden gnomes, and neighbours who talk to swamp spirits. She doesn’t care. She will not be moved. And reality seems to respect that.

    \subsection{Appearance}
    Button-up blouses, floral cardigans, and a perfect silver perm. Always seen with her trusty rolling pin and a suspiciously bottomless tote bag. Smells like lavender, fresh dough, and defiance.

    \subsection{Personality}
    Practical, no-nonsense, and immune to drama. She’s not rude, just extremely firm in her conviction that things will behave—whether they’re people, spirits, or carnivorous lawn chairs. Underneath her crusty exterior is someone who cares deeply. She just shows it by judging your posture and feeding you pie.

    \subsection{Connection to Dusty Pines}
    Owns Lot 3 and maintains the community herb garden (which occasionally tries to bite people). Nobody’s sure why she hasn’t been cursed yet. Edna thinks she’s “resonantly dull.” Tito avoids her.

    \subsection{Goals}
    To preserve order, protect her neighbours, and one day bake a pie so good it shuts Edna up for a full minute.

    \begin{WyrdStatsBlock}[profile=img/characters/linda_mae]

        \begin{SkillsBox}
            \Expert & Will \\
            \Skilled & Empathy, Crafts \\
            \Novice & Notice, Grit, Provoke
        \end{SkillsBox}

        \begin{TraitsBox}
            \item[“I Don’t Believe In That Nonsense”] — +2 to Will or Grit when resisting supernatural effects, illusions, or reality-warping nonsense.
            \item[Grandma Glare] — Once per session, shut down a supernatural threat with a single, withering look (Works best on ghosts. And teenagers.)
            \item[Bottomless Tote Bag] — Once per session, declare you have “just the thing” in your bag and pull out something unexpectedly useful.
        \end{TraitsBox}

        \begin{GearBox}
            \item[Iron-Rimmed Rolling Pin] — +2 to Provoke or Crafts when asserting dominance over cursed objects or uppity magical beings.
            \item[Banana Bread of Fortitude] — Once per session, share a slice to remove one Fatigue box from an ally.
            \item[The Mundane Aura] — Nearby magic has trouble functioning correctly. Sometimes this helps. Sometimes… not so much.
        \end{GearBox}

        \DamageBox

    \end{WyrdStatsBlock}
\end{WyrdCharacterSheet}

\begin{multicols}{2}