
\begin{WyrdScenarioHeading}{Murder at the Brass Orchid}
	The investigators are called to \textbf{The Brass Orchid}. The establishment is filled with wealthy patrons, performers, and staff—each with their own secrets to hide. The club’s reputation is at stake, and the clock is ticking before the police arrive to sweep things under the rug.

	The players must piece together the events of the evening, question patrons and staff, analyse the crime scene, and determine who had the means, motive, and opportunity to commit the crime. However, the deeper they dig, the more they realise that this murder is just the tip of the iceberg.

	\subsection*{Premise} 
	A high-society soirée at the exclusive cabaret, The Brass Orchid, is cut short when a well-connected financier is found dead in a locked room. The party was attended by the city's elite, but none saw the murder happen—or so they claim. The investigators must navigate a world of secrets, deception, and hidden rivalries to uncover the truth.

	\subsection*{What Really Happened} 
	\textbf{Beatrice Langley}, a hostess at The Brass Orchid, killed the financier, \textbf{Edward Mercer}, to protect herself from blackmail. Mercer had uncovered details about Beatrice’s past life and was threatening to expose her unless she paid a steep price. Desperate and out of options, she poisoned his drink and used the club’s pneumatic tube system to dispose of the evidence. However, a miscalculation led to certain clues being left behind.
\end{WyrdScenarioHeading}

\begin{WyrdGmTips}
	The suggested passive opposition rolls in the following are only that, suggestions. Feel free to adjust the difficulty based on the investigators' actions, skills, and the pace of the game. Remember that the goal is to keep the story moving forward, not to bog it down with unnecessary obstacles.
\end{WyrdGmTips}


\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/npcs/beatrice-langley}
\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/npcs/edward-mercer}

\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/act-0}
\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/act-1}
\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/act-2}
\input{content/episodic/grand-casebook/murder-at-the-brass-orchid/act-3}

\subsection{Resolutions} 
Depending on how the investigators handle the case, different outcomes may occur:
\begin{itemize}
	\item \textbf{Justice Served}: Beatrice is arrested or confesses, ensuring the truth is revealed.
	\item \textbf{A Deal in the Shadows}: The investigators allow Beatrice to flee, leveraging her knowledge for future gain.
	\item \textbf{The Wrong Culprit}: A scapegoat is framed, or the authorities arrest someone else entirely.
	\item \textbf{A Mystery Unsolved}: The players fail to piece everything together, leaving The Brass Orchid haunted by unanswered questions.
\end{itemize}

Regardless of the resolution, this case's events ripple across London’s elite, setting the stage for future intrigues.
