\begin{WyrdScenarioHeading}[The HOA Rises]{The HOA Rises}
    \label{scenario:hoa-rises}
    \index{The HOA Rises}
    \index{Scenario!The HOA Rises}

    Just when Dusty Pines thought it had weathered the last magical mishap, a new threat emerges—not with claws or curses, but with clipboards and citations. An ancient Homeowners Association, long believed dead (or at least disbanded), has mysteriously reactivated. Magical fines start appearing on doors. Gnome placement violations are magically enforced. And worst of all, someone has begun repainting trailers... beige.

    The players are drawn into a battle not just for survival, but for the soul of Dusty Pines. If they don’t stop this bureaucratic uprising, their delightfully weird neighborhood might become a perfectly regulated suburban nightmare. It’s time to stand against the HOA—and maybe fill out a few forms along the way.

    \subsection*{Premise}
    An ancient, magically binding HOA charter has reawakened, and Dusty Pines is under siege by enchanted citations, lawn décor regulations, and supernatural conformity spells. The players must investigate the source, outmaneuver the HOA’s magical enforcement, and stop the final ritual before Dusty Pines becomes a pastel-coloured suburban prison.

    \subsection*{Goals for the Players}
    \begin{itemize}
        \item Investigate the reactivation of the HOA and uncover who or what brought it back.
        \item Survive and subvert magically enforced citations, conformity spells, and HOA summons.
        \item Disrupt the HOA’s “Perfect Compliance” ritual and return Dusty Pines to its chaotic, loveable weirdness.
    \end{itemize}

    \subsection*{Atmosphere \& Tone}
    This scenario plays up the horror of bureaucracy with absurdist magical flair. Think cursed filing cabinets, spectral rulebooks, and HOA bylaws older than the Constitution. Expect a balance of supernatural mystery and comedic satire, with plenty of room for ridiculous player solutions. Let the park’s weirdness shine—and let the paperwork fly.
\end{WyrdScenarioHeading}

This scenario begins with a creeping sense of order—unnatural, shimmering, and deeply unsettling. Let the players soak in the rising tension as Dusty Pines slowly transforms into a picture-perfect suburban nightmare. From oddly stacked lawn chairs to mysteriously altered décor, the early signs of magical enforcement should feel subtle at first… then escalate quickly. Encourage the players to act before the trailer park’s unique charm is scrubbed clean by arcane bureaucracy.


\subsection{The First Violation Notice}

The trouble begins on a suspiciously quiet morning, when residents awaken to find glowing parchment citations magically affixed to their trailers.

\begin{center}
\fbox{\parbox{0.85\linewidth}{
    \centering
    \textbf{\Large NOTICE OF NONCOMPLIANCE}\\
    \smallskip
    \textbf{Violation: Improper Lawn Ornament Placement} \\
    \textbf{Fine: 12 Silver Acorns (Payable Immediately)} \\
    Failure to comply will result in enchanted correction and/or community service in the Form Reproduction Pits.  
    \medskip\\
    \textit{— Issued under Authority of the Dusty Pines Homeowners Association}
}}
\end{center}

Most residents laugh it off—until a wayward gnome statue is magically hurled back into alignment with an audible “clang.” Then the lawn chairs start stacking themselves. And someone’s trailer mysteriously gets a new beige paint job... overnight.

\textbf{Bobby the Befuddled} calls an emergency “sit-around” at his trailer, holding up a crumpled old document titled \textbf{“Original HOA Covenant – DO NOT RE-ACTIVATE.”} He swears it wasn’t him. Probably.

The players are asked to investigate who—or what—is bringing the HOA back to life, and how to stop it before Dusty Pines becomes a pastel, paved-over dystopia.

\subsection{Citation Station}

The players begin their investigation by examining the bizarre violations issued across the trailer park. Gnome rotations, garden flamingo spacing, and “curb appeal rituals” have all become matters of magical enforcement — complete with glowing warnings and subtle reality-warping effects.

\subsubsection*{What the Players Discover}
By interviewing neighbors and inspecting their own citations, the players uncover several oddities:

\begin{itemize}
    \item The citations are written in enchanted ink that glows faintly under moonlight and smells faintly of bureaucracy.
    \item Several residents have already experienced “compliance adjustments,” such as:
    \begin{itemize}
        \item Lawn ornaments forcibly rearranged into symmetrical patterns.
        \item Curtains replaced with HOA-approved beige blinds overnight.
        \item A trailer that began humming elevator music until someone filed an appeal form.
    \end{itemize}
    \item A mysterious magical energy seems to be radiating from the center of the park — possibly from the long-abandoned HOA trailer near Lot 0, which was supposed to have collapsed years ago.
\end{itemize}

\subsubsection*{Things the Players Can Try}
\begin{itemize}
    \item \textbf{Trace the Citations:} Using \textbf{Lore} or \textbf{Notice} \DL{+1}, the players can detect a faint magical signature that points toward the abandoned HOA trailer.
    \item \textbf{Talk to a Cursed Neighbor:} Find someone who’s been hit by multiple violations — like Harold “Hazard” Haddock — and hear what happened when he tried to resist.
    \item \textbf{Try to Void a Citation:} Attempt to burn, rip, or cast a spell on a citation — but beware: this may result in instant magical retaliation (e.g., getting slapped by flying paperwork or momentarily transformed into a HOA board member).
\end{itemize}

\begin{CommentBox}{Optional Chaos}
Hazard Haddock has a secret stash of old HOA forms he’s been hoarding since the '70s. If the players dig through it, they might find:
\begin{itemize}
    \item A loophole allowing residents to petition for “Discontinuance of Spirit-Led Enforcement” via majority vote.
    \item A summoning circle for the HOA president — half-burned, poorly erased, and definitely still active.
\end{itemize}
\end{CommentBox}


\subsection{The HOA Trailer (a.k.a. The Compliance Nexus)}

Following the trail of magical citations and escalating weirdness, the players are eventually led to Lot 0 — an overgrown patch of land behind the laundromat where no one’s parked in decades. At the center stands the old HOA trailer, half-sunken into the earth and overgrown with ivy, morning glory, and what appears to be enchanted crabgrass.

A rusted sign dangles over the door:
\begin{center}
\fbox{\parbox{0.8\linewidth}{
    \centering
    \textbf{DUSTY PINES HOA HEADQUARTERS}\\
    \textit{“Order, Cleanliness, Obedience” Since 1969}
}}
\end{center}

\subsubsection*{Exploring the Trailer}
Inside, the trailer is far larger than it appears from the outside — it warps space, bending into an impossible maze of filing cabinets, bureaucratic sigils, and floating paper forms. Players who step in feel a faint pull toward conformity. Their clothes may iron themselves. Hair styles attempt to part neatly. One player may briefly begin craving sensible beige slacks.

\textbf{Possible discoveries:}
\begin{itemize}
    \item A glowing, floating registry book constantly writes new citations in real time. If destroyed or stolen, it slows enforcement across the park.
    \item A locked vault labeled “Founding Documents – DO NOT OPEN.” Cracking it (with \textbf{Crafts} or \textbf{Burglary} \DL{+2}) reveals the magical contract that powers the HOA — a document binding all residents to arcane codes unless nullified by community vote.
    \item A haunted nameplate reads \textbf{“President Cynthia Clench, HOA Eternal”} — it pulses with magical energy, indicating she’s not only active but gaining power.
\end{itemize}

\subsubsection*{Confrontation with Cynthia}
If the players linger too long or tamper with the wrong drawer, Cynthia Clench herself may manifest in a swirl of administrative energy — a ghostly, pinched figure in pearls and pastels, wielding a radiant clipboard and a terrifying smile.

She will:
\begin{itemize}
    \item Deliver a polite but chilling warning about noncompliance.
    \item Offer the players a "voluntary reeducation pamphlet" (which bites).
    \item Hint that the final phase — “Total Park Harmonization” — is already underway.
\end{itemize}

\begin{CommentBox}{Player Choices}
Players can try to:
\begin{itemize}
    \item Sneak out with the founding charter.
    \item Bargain with Cynthia — though she only respects correctly filed motions.
    \item Disrupt the trailer’s enchantment by planting symbols of chaos (e.g. glitter, flamingo statues, or a live gremlin).
\end{itemize}
\end{CommentBox}

\end{multicols}
\clearpage
\begin{multicols}{2}

\begin{NPC}[description={Rulebreaking, Loud, Unflinchingly Proud}]{Harold “Hazard” Haddock}

    Harold “Hazard” Haddock has been violating HOA bylaws since before they were even written down. Loud, stubborn, and proudly unkempt, Hazard believes personal freedom is measured in how many pink flamingos you can fit on your roof. He sees the return of the HOA as a personal challenge and is absolutely ready to fight magical bureaucracy with barbeque tongs and duct tape.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Expert & \textbf{Provoke} \\
        \Skilled & \textbf{Will}, \textbf{Crafts} \\
        \Novice  & \textbf{Athletics}, \textbf{Lore}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Chronic Noncompliance] Immune to minor magical enforcement effects (he’s been hexed so many times he’s basically acclimated).
        \item[Barbeque Battle Strategist] +1 to overcome or create advantage when turning ordinary household junk into makeshift resistance tools.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=3,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}

\begin{NPC}[description={Bureaucratic, Passive-Aggressively Powerful}]{Cynthia Clench}

    Cynthia Clench was once the iron-willed president of the Dusty Pines HOA. In death, she has only grown stronger. Bound to the original charter by ancient bureaucratic magic (and possibly spite), she enforces conformity with ghostly precision. Always calm, always polite, Cynthia manifests in pastel power-suits and emits a faint scent of lemon pledge and fear.

    She is not openly violent—but the enchantments she controls are vast, subtle, and increasingly dangerous.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Expert & \textbf{Will} \\
        \Skilled & \textbf{Lore}, \textbf{Provoke} \\
        \Novice  & \textbf{Deceive}, \textbf{Empathy}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Bylaw Enforcement Aura] While Cynthia is present, players attempting to break rules or resist magical citations take \textbf{–1 to all overcome actions} unless they succeed on a \textbf{Will} check \DL{+1}.
        \item[Administrative Poltergeist] Cynthia can animate paperwork, filing cabinets, and outdated computers to harass, entangle, or distract intruders.
        \item[Perfectly Composed] Immune to emotional manipulation and intimidation. May sigh disapprovingly instead.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=3,%
        totalmild=1,totalmoderate=1,totalsevere=1,%
    ]
\end{NPC}

\end{multicols}
\clearpage
\begin{multicols}{2}


\subsection{The Conformity Field Expands}

As the HOA’s influence spreads, Dusty Pines begins to change—visibly and unnervingly. Strange magical effects ripple through the park, slowly sanding off its edges and replacing them with bland uniformity.

\subsubsection*{Signs of the Field}
The players begin noticing signs that reality itself is being reshaped:
\begin{itemize}
    \item Trailers begin shifting into identical layouts, sprouting white picket fences overnight.
    \item Lawn flamingos line up in formation, and gnomes salute as the players pass.
    \item Music from nearby radios and TVs becomes eerily identical—elevator jazz with no discernible source.
    \item Residents feel compelled to tuck in their shirts, mow lawns with exact symmetry, or sort their recyclables alphabetically.
\end{itemize}

\subsubsection*{Mechanics}
While inside the Conformity Field:
\begin{itemize}
    \item Players take \textbf{–1 to any action involving creativity, rebellion, or chaos} unless they succeed on a \textbf{Will} check \DL{+1}.
    \item Magical effects become muted or altered unless they are “orderly” in nature (e.g., illusions manifest as tidy charts or office clip art).
    \item Gremlins, ghosts, and other supernatural residents either flee or become eerily well-behaved.
\end{itemize}

\subsubsection*{How to Push Back}
Players can attempt to disrupt the field temporarily through acts of joyful rebellion:
\begin{itemize}
    \item Host a spontaneous dance party.
    \item Flood the airwaves with chaotic trailer park radio.
    \item Build an illegal monument out of flamingos and lawn chairs.
\end{itemize}

These acts may weaken the HOA’s hold, inspire other residents to resist, and earn mechanical boosts for the final confrontation.


\subsection{Rallying the Resistance}

The players can’t stop the HOA alone—but not all is lost. Some residents have begun to quietly rebel: painting their mailboxes garish colours, putting gnome hats on their cats, and hosting “illegal” potlucks full of spicy food and unsanctioned laughter. With the right push, the players can unite these chaotic spirits into an HOA-fighting force.

\subsubsection*{Key Allies}
\begin{itemize}
    \item \textbf{Hazard Haddock} is already stockpiling “anti-compliance gear” (BBQ skewers, glitter bombs, and lawn darts). If approached, he offers to lead a “Task Force of General Mayhem.”
    \item \textbf{Edna the Bog Witch} claims she’s neutral—but may offer a ritual of disorder if bribed with a good casserole and at least one ridiculous promise.
    \item \textbf{Rusty the Gnome Whisperer} can rouse the gnomes to active rebellion, but only if someone convinces them their freedom is at stake (they’re oddly fond of beige).
\end{itemize}

\subsubsection*{What the Players Can Do}
To organize a meaningful resistance, players must gather residents, inspire rebellion, and choose a plan of action:

\begin{itemize}
    \item \textbf{Hold an Emergency Town “Dishall” Meeting}: Set up a flamingo-lit circle in the park after curfew. Use \textbf{Rapport} \DL{+1} to rally support.
    \item \textbf{Create the Chaos Manifesto}: A magically resonant protest banner or proclamation, full of jokes, glitter, and deliberate typos. This counts as a magical counter-sigil and may weaken the HOA’s control if displayed.
    \item \textbf{Distribute Rebellion Kits}: Flyers, rogue spells, gremlin-snack traps, and home-brewed confusion potions. (Edna’s are especially fun if a bit unstable.)
\end{itemize}

\subsubsection*{Outcome}
If successful, the players assemble a full-scale neighborhood rebellion—ready to launch a final strike at the HOA's headquarters just before the “Perfect Compliance” ritual is finalized.

\begin{CommentBox}{Optional Twist}
    One loyalist (perhaps a brainwashed resident or Cynthia’s spectral intern) may try to sabotage the meeting. Catching them in the act earns a morale boost.
\end{CommentBox}


\subsection{The Ritual of Perfect Compliance}

The HOA’s ultimate plan is nearly complete. At the stroke of midnight, Cynthia Clench will activate the long-dormant Ritual of Perfect Compliance—a magical spell woven into the original HOA charter that will lock Dusty Pines into eternal regulation. If it succeeds, no flamingo will ever stand out of line again.

\subsubsection*{The Setting}
The final ritual takes place in the magically expanded HOA trailer, which now resembles a glowing suburban office complex filled with floating clipboards, levitating filing cabinets, and softly humming beige walls. At its centre, a podium rises before a giant holographic bylaw wheel, slowly turning toward “PERMANENT ENFORCEMENT.”

\textbf{Defensive enchantments are active:}
\begin{itemize}
    \item Anyone speaking out of turn takes a \textbf{–1 penalty} to actions for one round.
    \item All magic with “chaotic” or “unsanctioned” descriptors requires a \textbf{Lore} \DL{+2} check to function normally.
\end{itemize}

\subsubsection*{Disrupting the Ritual}
To stop Cynthia and her bureaucratic magic from taking hold permanently, players can choose several approaches:

\begin{itemize}
    \item \textbf{Overload the Ritual Matrix:} Plug in too many nonconforming documents—like Rusty’s glitter protest fliers or the Chaos Manifesto—to corrupt the enchantment's logic. (\textbf{Crafts} or \textbf{Lore} \DL{+2})
    \item \textbf{Challenge the Bylaw in Council:} Invoke the park’s oldest magical clause—a community vote. Players must convince residents to oppose the ritual on the spot. (\textbf{Rapport}, \textbf{Provoke}, or \textbf{Will} \DL{+1 per resident})
    \item \textbf{Battle Cynthia Directly:} Confront the spectral president in a magical showdown of personality, improvisation, and deeply petty rule-lawyering.
\end{itemize}

\subsubsection*{Cynthia's Response}
If disrupted, Cynthia will:
\begin{itemize}
    \item Summon spectral assistants to shuffle paperwork and toss magical citations.
    \item Attempt to reset the ritual with emergency HOA protocols.
    \item Target the most flamboyantly chaotic player with the spell \textbf{“Mandated Neutral Palette.”}
\end{itemize}

\begin{CommentBox}{Victory Conditions}
    The ritual ends if any of the following occur:
    \begin{itemize}
        \item The original charter is destroyed in a blaze of community spirit (or barbecue fire).
        \item A majority of Dusty Pines residents vocally object and vote to nullify the HOA.
        \item Cynthia is convinced (or tricked) into retiring permanently.
    \end{itemize}
    If none of these happen, Dusty Pines becomes a bland suburban nightmare—until someone breaks the spell in a future adventure.
\end{CommentBox}


\subsection{Ending the Scenario}

With the ritual stopped—or not—the fate of Dusty Pines rests in the players’ hands. Depending on how events unfold, the conclusion can take many forms:

\subsubsection*{If the Ritual Is Disrupted}
The enchantment collapses in a spectacular display of sparking paperwork and wilting beige vines. Cynthia Clench lets out a long, disappointed sigh and dissolves into lemon-scented mist. The HOA trailer implodes back into its original rusted state.

\textbf{Results:}
\begin{itemize}
    \item Residents regain their individuality (some more enthusiastically than others).
    \item Bobby declares a park-wide “Weirdness Appreciation Day,” which involves tacos, glitter, and possibly a celebratory possum parade.
    \item Players gain the lasting admiration of the trailer park — and perhaps a few grumbling curses from surviving HOA spirits.
\end{itemize}

\subsubsection*{If the Ritual Partially Succeeds}
Maybe the players won… mostly. The HOA’s power is weakened but not gone. Some parts of the park remain oddly uniform, and monthly meetings are now magically enforced (with donuts). Cynthia may return… with red tape reinforcements.

\textbf{Results:}
\begin{itemize}
    \item Players earn a temporary reprieve but will need to stay on their toes.
    \item Some residents embrace the changes, leading to awkward “suburban supremacy” factions.
    \item The park is safe — for now — but the battle for Dusty Pines’ soul isn’t over.
\end{itemize}

\subsubsection*{If the Ritual Succeeds}
Dusty Pines falls into order. Lawn flamingos wear uniforms. Gnomes march in formation. Every trailer is beige. Cynthia rules with a gentle but ironclad HOA smile. The players may need to spark a future rebellion from within.

\textbf{Results:}
\begin{itemize}
    \item The scenario ends on a dystopian note (but one ripe for a sequel).
    \item Characters who resist too hard may be reassigned to “compliance training.”
    \item Optional cliffhanger: Hazard disappears underground, forming a secret resistance.
\end{itemize}

\begin{CommentBox}{Future Hook}
    Cynthia may have been defeated, but the HOA’s charter still exists. If not destroyed, it could fall into other hands—or awaken in a different trailer park. It might even be sold on Etsy.
\end{CommentBox}


