% !TeX root = ../../../../wyrd.tex


\begin{WyrdScenarioHeading}[Fangs, Fur, and Fugitives]{Fangs, Fur,\\ and Fugitives}
    \label{scenario:fangs-fur-fugitive}
    \index{Fangs, Fur, and Fugitives}
    \index{Scenario!Fangs, Fur, and Fugitives}

    Things have been quiet lately at Dusty Pines — well, as quiet as a trailer park full of enchanted lawn furniture and talking raccoons can get. But the moment a beautifully restored vintage RV rolled into the far lot, residents started whispering. The new couple? Charming. Mysterious. Only active after dark. One wears a lot of velvet. The other could probably bench-press a food truck. Something’s clearly up.

    That “something” is Victor von Fennel and Lyla Greyfur — an elderly vampire and a retired werewolf, trying to settle down after a long, chaotic life on the run. But trouble has followed them to Dusty Pines in the form of Marlena Steele, a relentless monster hunter with a grudge, a plan, and way too many silver-tipped crossbow bolts.

    The players must uncover Marlena’s true identity, protect their new neighbors from exposure or worse, and help Dusty Pines survive yet another supernatural showdown without waking up the entire neighborhood (again).

    \subsection*{Premise}
    A vampire and a werewolf have retired to Dusty Pines seeking peace. But an old enemy has followed them, determined to bring them down. The players must navigate secrecy, subterfuge, and park politics to protect their new neighbors before things turn into a monster movie massacre.

    \subsection*{Goals for the Players}
    \begin{itemize}
        \item Identify and outmaneuver Marlena Steele before she finds her targets.
        \item Build trust with Victor and Lyla so they’ll accept help.
        \item Protect the couple (and the park) through deception, distraction, or confrontation.
    \end{itemize}

    \subsection*{Atmosphere \& Tone}
    This scenario blends gentle gothic flair with Dusty Pines absurdity. Expect spooky comedy, heartfelt moments between retirees with secrets, and escalating tension as the hunter gets closer. Think of it as *What We Do in the Shadows* meets *Cocoon*… if both took place behind a gas station.
\end{WyrdScenarioHeading}

This scenario leans into paranormal slice-of-life with a side of suspense. While the stakes may rise, the heart of the story is about trust, chosen family, and what it means to start over when you’ve lived a thousand lifetimes (or just had one really intense supernatural midlife crisis). Encourage moments of quiet connection, tense cat-and-mouse antics with the hunter, and just enough park gossip to keep things spicy. Let the players lead the tone—whether they want to run recon with a raccoon militia or stage a theatrical fake death—Dusty Pines has room for it all.

The scenario is centered on a new couple moving in, with various independent complications that the players can engage in (and that can be run in any order), and with one larger plot arc where the players must deal with the hunter \textbf{Marlena Steele}.

\subsection{The New Neighbors}

It’s early evening when the players are summoned to Bobby’s trailer for an “important neighborly update.” He’s clearly flustered, standing in front of a dry-erase board that says 
\begin{center}
    \fbox{\parbox{0.85\linewidth}{
        \centering
        \textbf{\large WELCOME VICTOR \& LYLA???} \\[0.5em]
    }}
\end{center}
in multiple colors and underlined four times. (Someone tried to add a smiley face but gave up halfway through.)

\subsubsection*{What Bobby Knows}
\begin{itemize}
    \item A new couple moved in last night. Rented Lot 23. Paid three months in advance. No trouble so far.
    \item Their RV is spotless. Like, weirdly spotless. Like “buffed with vampire spit” spotless.
    \item They only come out after dark. Bobby isn’t judging, but he’s also scared of velvet.
    \item Some residents are already spreading rumors, especially Rusty, who swears he saw one of them hiss at a bug zapper.
\end{itemize}

Bobby wants the players to make a good impression (he’s trying to get the park featured on a paranormal-friendly housing registry), but he also wants them to keep an eye out for… you know. “Unnatural incidents.” Just in case.

\subsubsection*{First Impressions at Lot 23}
Victor and Lyla are seated under the awning of their pristine vintage RV. Victor is sipping something from a stemmed goblet (tomato juice, allegedly) and Lyla is carving a bone-handled back scratcher with unsettling precision. A cat with a lazy eye is asleep across both their laps.

\textbf{Victor von Fennel} is pale, polite, and vaguely theatrical. He speaks like a man who once gave monologues to mirrors.  
\textbf{Lyla Greyfur} is gruff, practical, and protective—but has a warm side that peeks through when she sees kindness.

\subsubsection*{How the Players Can Engage}
\begin{itemize}
    \item \textbf{Make a Good Impression:} A successful \textbf{Rapport} or \textbf{Empathy} check \DL{+1} shows the couple the players are trustworthy.
    \item \textbf{Get Suspicious Info:} With \textbf{Notice} or \textbf{Lore} \DL{+1}, players spot garlic charms around the RV (as jokes) and a silver bracelet Lyla keeps in her pocket—just in case.
    \item \textbf{Offer Help:} If players ask about any trouble, Victor politely brushes it off—but his eyes dart toward the woods as he mentions “an old acquaintance who doesn’t know how to quit.”
\end{itemize}

\begin{CommentBox}{Optional Escalation}
    Just as the conversation is winding down, a hawk-shaped drone buzzes overhead. Lyla squints. Victor frowns. And in a nearby bush, someone in a beige sunhat quietly takes notes. The hunt has begun.
\end{CommentBox}

\subsection{Secrets Under Moonlight}

Victor and Lyla may be retired, but secrecy is a hard habit to break. They don’t reveal their true nature lightly — but with the players’ kindness, persistence, or a well-timed emergency, the truth eventually comes out. Whether the players earn their trust or stumble into the truth, one thing becomes clear: the couple is anything but ordinary.

\subsubsection*{Ways to Trigger the Reveal}
\begin{itemize}
    \item \textbf{Build Trust:} A player succeeds at a \textbf{Rapport} or \textbf{Empathy} roll \DL{+2} during a personal conversation at Lot 23.
    \item \textbf{Catch a Glimpse:} A failed \textbf{Stealth} check (Victor) or a transformation slip (Lyla) reveals something supernatural.
    \item \textbf{Emergency Reaction:} During a park mishap (gremlin scare, trash fire, etc.), Victor or Lyla uses their powers to protect someone, revealing their identity.
\end{itemize}

\begin{Example}{The Reveal}
    Victor sets down his goblet and straightens his collar. “Very well. Cards on the table.”

    Lyla shrugs. “We’re supernatural. He’s a vampire. I’m a werewolf. Retired, mostly. Don’t make a big deal of it.”

    Victor adds, “We’ve been on the run for... oh, decades now. From someone who thinks we’re monsters. We’re tired. Dusty Pines is the first place that’s felt... restful.”

    Lyla nods. “And we’d like it to stay that way.”
\end{Example}

They explain they’ve hurt no one in years and want nothing more than peace, privacy, and the occasional full moon jog (with supervision). They’ve grown weary of hiding, but trust doesn’t come easily.

\subsubsection*{How the Players Can Respond}
\begin{itemize}
    \item \textbf{Supportive Response:} The couple opens up further, offering insights, sharing supernatural advice, or even providing low-level magical help.
    \item \textbf{Skeptical Response:} Lyla goes quiet. Victor becomes evasive. Trust will need to be earned again.
    \item \textbf{Offer Protection:} Players who offer to help keep their secret gain access to future plot hooks and a powerful ally when things go wrong.
\end{itemize}

\begin{CommentBox}{Roleplaying Tip}
    Encourage players to ask questions. This can be a heartfelt moment of connection, or an awkwardly comedic one as the players process the idea of having a vampire-werewolf power couple for neighbors.
\end{CommentBox}


\subsection{Nosy Neighbors Stirring Trouble}

Dusty Pines is many things, but discreet isn’t one of them. With Victor and Lyla’s habits raising eyebrows and Marlena skulking around with a camera, the neighborhood grapevine is in full bloom — and it’s about to cause problems.

\subsubsection*{The Suspects}
Several residents are poking around where they shouldn’t:
\begin{itemize}
    \item \textbf{Rusty the Gnome Whisperer} claims his garden gnomes have warned him about a “bloodsucker infestation.”
    \item \textbf{Charlene (“Chair-lene”)} swears she heard howling from Lot 23 — and she’s started collecting “silver teaspoons, just in case.”
    \item \textbf{Tito the Chupacabra} has been leaving chewed chicken bones on Victor’s porch — no one knows if it's a warning or a gift.
\end{itemize}

\subsubsection*{Player Challenges}
\begin{itemize}
    \item \textbf{Distract or Misdirect} – Convince neighbors there’s a more exciting park drama happening elsewhere (e.g., claim Edna’s brewing a love potion for Bobby).
        \begin{itemize}
            \item \textbf{Deceive or Rapport} \DL{+1}
        \end{itemize}

    \item \textbf{Reassure the Residents} – Calm fears about "monsters" by spinning a tale about Lot 23 being a “celebrity ghost tour stop” or “sleep study participants.”
        \begin{itemize}
            \item \textbf{Provoke or Empathy} \DL{+1}
        \end{itemize}

    \item \textbf{Redirect Curiosity} – Offer an obvious distraction, like helping Edna organize a public “Potion Clearance Sale” or staging a fake gnome wedding.
        \begin{itemize}
            \item \textbf{Crafts or Contacts} \DL{+1}
        \end{itemize}
\end{itemize}

\subsubsection*{Escalation Risk}
If the players fail to manage the neighbors, rumors may spread beyond the park. A concerned resident might call in a local paranormal podcast host, a true-crime TikToker, or even a nosy city official — any of which could draw unwanted attention to Victor and Lyla.


\subsection{Victor’s Blood Shortage}

Though Victor has long since sworn off human blood, he still needs to feed. Normally, he keeps a private stash of ethically sourced animal blood from specialty butchers, but due to all the moving, distractions, and a slight mishap with a leaky cooler, his supply is dangerously low.

Victor doesn’t want to alarm Lyla — or the players — but if he goes too long without feeding, even his well-honed self-control might start to fray.

\subsubsection*{Clues Something’s Wrong}
\begin{itemize}
    \item Victor seems unusually pale (even for him), sluggish, and irritable.
    \item He avoids social gatherings and refuses invitations to Edna’s latest potion-tasting party.
    \item Anyone who notices his stash fridge will find it nearly empty — a \textbf{Notice} or \textbf{Lore} \DL{+1} confirms this isn’t ideal for a vampire on a “low-guilt” diet.
\end{itemize}

\subsubsection*{How the Players Can Help}
Victor is too proud to ask for help, but if the players offer, he’ll reluctantly accept. Possible solutions include:

\begin{itemize}
    \item \textbf{Visit the Local Butcher:} The players might sneak into town and bribe, convince, or deceive a butcher into selling blood “for culinary reasons.”
        \begin{itemize}
            \item \textbf{Deceive, Resources, or Contacts} \DL{+1–2}
        \end{itemize}
    \item \textbf{Ask Edna:} Edna may have frozen goat blood (“for rituals, obviously”) — but she’ll want something in return.
        \begin{itemize}
            \item \textbf{Will or Empathy} \DL{+1} to haggle her down to something non-disastrous.
        \end{itemize}
    \item \textbf{Find a Donor:} One particularly odd resident offers their chicken’s blood “as long as Clarence gets a spa day afterward.” Convincing both chicken and owner could be a whole side quest.
        \begin{itemize}
            \item \textbf{Rapport or Provoke} \DL{+1}, and possibly \textbf{Animal Handling} (if you’re using a Trait or Skill for it).
        \end{itemize}
\end{itemize}

\subsubsection*{What Happens If They Fail}
If Victor doesn’t get his supply replenished:
\begin{itemize}
    \item He begins sleepwalking toward the local petting zoo with a hungry look in his eyes.
    \item He accidentally glamour-charmes a player while trying to borrow their energy “just a bit.”
    \item He starts baking — terribly — in an attempt to curb cravings. Blood-scented muffins are a *bad idea*.
\end{itemize}




\subsection{Lyla’s Full Moon Trouble}

The full moon is approaching, and while Lyla has her transformation mostly under control, “mostly” doesn’t mean “safely.” She hasn’t had a proper containment space since they moved to Dusty Pines, and Victor’s suggestion of “just meditating with herbal tea” didn’t go over well.

Lyla needs somewhere secure, private, and ideally not full of bite-sized neighbors. If the players don’t help her prepare, the night could get hairy — literally.

\subsubsection*{What the Players Learn}
Lyla brings it up with deliberate awkwardness, perhaps while fixing her porch railing with one hand and sharpening her claws with the other.

\begin{Example}{}
    “So, uh... full moon’s in three nights. I usually run it out in the woods, but Victor says there’s too many possums around here. Got a plan?”
\end{Example}

She’s open about her condition but deeply uncomfortable asking for help. This is a matter of pride — and survival.

\subsubsection*{What the Players Can Do}
\begin{itemize}
    \item \textbf{Build a Containment Den:} Reinforce an old shed, trailer, or Edna’s unused potion cellar with locks, charms, and maybe a calming playlist.
        \begin{itemize}
            \item \textbf{Crafts or Lore} \DL{+1}
        \end{itemize}
    \item \textbf{Secure the Area:} Make sure no one wanders in during the transformation. Distract Tito, post warning signs, or convince Chair-lene that “the shed is full of spiders.”
        \begin{itemize}
            \item \textbf{Stealth, Deceive, or Rapport} \DL{+1}
        \end{itemize}
    \item \textbf{Offer Emotional Support:} Be present. Bring snacks. Remind Lyla she’s not alone.
        \begin{itemize}
            \item \textbf{Empathy} \DL{+1}
        \end{itemize}
\end{itemize}

\subsubsection*{Optional Complications}
\begin{itemize}
    \item The players forget to reinforce the door hinges. Lyla breaks out mid-transformation and howls “FREEEEDOMMM” before fleeing into the park wearing a tutu.
    \item Edna drops by uninvited to “borrow sugar” and gets chased off by were-Lyla in a mood.
    \item Rusty tries to livestream the event, thinking it’s a "gnome summoning rite."
\end{itemize}

\begin{CommentBox}{Nice Reward}
    If the players help Lyla feel safe and respected, she opens up emotionally and may teach one of them a minor combat trick or share a tale from her wild youth — possibly involving a biker gang and a cursed jukebox.
\end{CommentBox}




\end{multicols}
\newpage
\begin{multicols}{2}
\subsection{A Hunter in Hiding}

A few weeks after Victor and Lyla reveal their secret, strange things start happening in Dusty Pines. Nothing overtly hostile — yet — but enough to raise eyebrows.

\subsubsection*{Signs of a Watcher}
The players may notice one or more of the following:

\begin{itemize}
    \item A hawk-shaped drone buzzes overhead, then disappears behind a cloud. No one in the park claims it.
    \item A strange woman in a beige sunhat is spotted strolling around with a camera, claiming to be a “freelance wildlife photographer.”
    \item Tito the chupacabra starts growling at a seemingly ordinary lawn chair near Lot 23.
    \item One of Edna’s wards goes off near the fence line — “too clean a break,” she mutters, “like someone who knows how to slip through magical security.”
\end{itemize}

\subsubsection*{Identifying Marlena}
The mysterious woman is, in fact, \textbf{Marlena Steele}, a seasoned monster hunter with decades of fieldwork behind her. She’s clever, quiet, and dangerous. She's not attacking—yet. She's watching.

\textbf{How the players might identify her:}
\begin{itemize}
    \item \textbf{Contacts or Lore} \DL{+2} — Recognize the name or her signature gear (silver jewelry, scent-masking herbs, or the crossbow under her trench coat).
    \item \textbf{Deceive or Rapport} \DL{+1} — Engage her in conversation and catch a slip, such as using terminology only a hunter would know.
    \item \textbf{Stealth or Notice} \DL{+1} — Follow her to a hidden observation post in an abandoned RV outside the park.
    \item \textbf{Just ask Victor and Lyla} — They know her name and can provide a brief history. Victor is wary, but Lyla is more open to discussing their past.
\end{itemize}

\subsubsection*{Marlena’s Behaviour}
Marlena won’t make the first move until she’s sure of her targets. She’s polite but cool, collecting information and testing residents’ reactions. If pressed too hard, she’ll disappear for a day or two before returning even more cautious.

If the players ignore her too long, Marlena may leave a note at Bobby’s office reading:  
\begin{center}
    \fbox{\parbox{0.8\linewidth}{
        \centering
        \textbf{“You don’t know who you’re protecting. They don’t stop being dangerous just because they’re old.”}
    }}
\end{center}

\subsubsection*{Player Objectives}
\begin{itemize}
    \item Identify Marlena without tipping her off.
    \item Determine how much she knows about Victor and Lyla.
    \item Decide whether to mislead her, confront her, or prepare for a more direct conflict.
\end{itemize}

\begin{NPC}[description={Hunter, Focused, Not Easily Fooled}]{Marlena Steele}

    Marlena Steele has been tracking supernatural beings for over thirty years. Tall, weathered, and sharp-eyed, she dresses like someone who’s always ready for a fight — or a nature hike. She believes Victor and Lyla are dangerous, no matter how "retired" they claim to be. Calm under pressure and relentless in pursuit, she operates alone and always trusts her instincts.

    Her trailer is parked just outside Dusty Pines — camouflaged and lined with anti-supernatural wards. She’s watching. Waiting. And armed to the teeth with silver, salt, and an old grudge.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Skilled & \textbf{Notice}, \textbf{Shoot} \\
        \Novice  & \textbf{Stealth}, \textbf{Will}, \textbf{Deceive}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Hunter’s Focus] Once per scene, Marlena can reroll a failed \textbf{Notice} or \textbf{Shoot} check if pursuing a supernatural target.
        \item[Prepared for Anything] She always has the right gear — silver bolts, enchanted snares, or blessed salt. Gain +1 on actions where specialized gear gives her the edge.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=3,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}


\subsection{Marlena’s Trap}

If the players haven't dealt with Marlena Steele on their own accord, it is time for the GM to push them a little. Marlena will wait until the perfect moment. When the neighbors are distracted, the trap is sprung.

\subsubsection*{How It Begins}
The players receive a panicked message from Bobby:  
\begin{center}
\fbox{\parbox{0.8\linewidth}{
    \centering
    \textbf{“CODE GLITTER! Repeat, CODE GLITTER! There’s a tripwire near Edna’s flamingos, and Victor just collapsed!”}
}}
\end{center}

\textbf{Victor} has triggered a hidden sigil on the path near Lot 23 — a magically primed anti-vampire ward laced with silver shavings.  
\textbf{Lyla} rushes to help him, but more traps line the perimeter: silver nail strips, scent-masking fields, and a collapsible net laced with salt. These are not amateur tools — Marlena has come prepared for a takedown.

\subsubsection*{What the Players Must Do}
\begin{itemize}
    \item \textbf{Get Victor to Safety:} He’s weakened by the ward and needs help escaping the trap site.
        \begin{itemize}
            \item \textbf{Physique or Will} \DL{+2} to carry or support him.
        \end{itemize}
    \item \textbf{Disarm Traps Around the Park:} Remove, disable, or reroute magical and physical traps without triggering more.
        \begin{itemize}
            \item \textbf{Lore or Crafts} \DL{+2} to disable magic traps. \textbf{Notice} or \textbf{Stealth} for spotting them in time.
        \end{itemize}
    \item \textbf{Confront Marlena:} She watches from across the road, calm and ready. She won’t attack first — but she’s here to end this.
\end{itemize}

\subsubsection*{How Confrontation Might Play Out}
\begin{itemize}
    \item \textbf{Negotiate a Ceasefire:} The players talk her down, using what they’ve learned to prove Victor and Lyla are harmless.  
        \begin{itemize}
            \item \textbf{Empathy, Will, or Rapport} \DL{+2} — this takes sincerity, logic, and maybe a little guilt-tripping.
        \end{itemize}
    \item \textbf{Outwit Her:} Trick her into chasing a decoy or luring her into one of her own traps.
        \begin{itemize}
            \item \textbf{Deceive or Stealth} \DL{+2}
        \end{itemize}
    \item \textbf{Stand and Fight:} If all else fails, the players can stand between Marlena and the couple. A tense combat may break out — but park residents (and possibly Tito) might come to their aid if they’ve built goodwill.
\end{itemize}

\subsubsection*{Optional Complication}
If the players hesitate or split up:
\begin{itemize}
    \item Marlena deploys silver flashbangs and tries to isolate Lyla.
    \item A warded net traps a player, forcing the others to choose: save the player, or stop Marlena.
    \item Rusty wanders into the crossfire yelling “Gnome rights are people rights!” and may accidentally save the day.
\end{itemize}

\subsubsection*{Possible Outcomes}
\begin{itemize}
    \item \textbf{Peace Brokered:} Marlena leaves, convinced (or reluctantly agreeing) that Victor and Lyla are no longer a threat. She may return in future scenarios.
    \item \textbf{Marlena Defeated:} If the players fight and win, Marlena is forced to retreat — but she’s now a recurring enemy.
    \item \textbf{Betrayal or Failure:} If the players falter or try to appease both sides, Marlena may capture one of the NPCs or leave Dusty Pines in disarray.
\end{itemize}

\begin{CommentBox}{Resident Intervention}
If the players made friends during the earlier scenes, other residents may show up to help:
\begin{itemize}
    \item Edna hurls a cursed casserole.
    \item Chair-lene deploys the Emergency Lawn Flamingos.
    \item Tito eats a trap — on purpose.
\end{itemize}
\end{CommentBox}

\subsection*{Ending the Scenario}

No matter how the confrontation plays out, life at Dusty Pines returns to something resembling normal — which, around here, still means weird.

If the players protected Victor and Lyla, they’ve earned the trust and gratitude of two powerful supernatural allies. The couple agrees to stay, quietly integrating into park life. Victor begins hosting dramatic readings of Gothic poetry on Thursday nights. Lyla starts a werewolf-friendly yoga class behind the laundry trailer. There’s talk of starting a neighborhood watch — but only after the next full moon.

\textbf{If Marlena was persuaded to leave:} She disappears into the night, leaving behind a note:  
\begin{center}
    \fbox{\parbox{0.8\linewidth}{
        \centering
        \textbf{“You bought them time. But someday, you’ll see I was right.”}
    }}
\end{center}

\textbf{If she was defeated:} She escapes, vowing revenge. She might show up again in future adventures — smarter, meaner, and less patient.

\textbf{If things went badly:} Victor and Lyla may be forced to flee again, disappearing before the players can stop them. Their trailer space remains vacant... but a thank-you note is taped to the door. “We’ll always remember Dusty Pines,” it says, “and the people who gave us a chance.”

\begin{CommentBox}{Reward Ideas}
\begin{itemize}
    \item A protective ward from Victor that gives +1 to defend against supernatural threats for one scene.
    \item A silver-fanged keychain from Lyla that howls faintly during full moons.
    \item A cryptic coupon from Edna: “Redeem for One Free Favor, No Questions Asked (Void During Eclipses).”
\end{itemize}
\end{CommentBox}

