
\begin{NPC}[description=The elite clientele of the Orchid]{The Patrons of the Brass Orchid}
	
    \emph{An exclusive mix of aristocrats, socialites, and shadowy figures seeking entertainment, influence, or illicit dealings. Many were present on the night of the murder—some more observant than others.}
        
	\subsubsection*{Lord Alistair Pembroke}
	Wealthy Industrialist – A steel magnate with an imposing presence, known for both his ruthless business tactics and his excessive gambling.  
	\textbf{What He Knows:} Pembroke had his own business to attend to at the tables, but he noticed Mercer acting smug and confident, calling for more drinks and toasting to "fortune smiling at last." 

	\subsubsection*{Genevieve Ashdown}
	Scandalous Socialite – A striking woman with a penchant for dangerous liaisons and whispered rumours. She thrives on court intrigue and nightlife gossip.
	\textbf{What She Knows:} Genevieve witnessed Beatrice and Mercer talking earlier in the night. She saw Beatrice grab Mercer’s wrist in desperation, pleading in hushed tones before Mercer simply laughed and pulled away.

	\subsubsection*{Dr. Elias Forsythe}
	Respected Physician – A surgeon with a growing reputation, attending the Orchid to enjoy his vices away from prying eyes.
	\textbf{What He Knows:} Dr. Forsythe noticed Beatrice downing a drink with shaking hands just before leaving for Mercer’s booth. He was too focused on his own affairs to linger, but he distinctly recalls her expression—not anger, but sheer dread.
\end{NPC}
