\begin{NPC}[description=The people who keep the Orchid running]{The Staff of the Brass Orchid}
	
    \emph{A well-oiled machine of waiters, bartenders, entertainers, and security staff, all working under the careful watch of Madame Duval. Each has their own secrets—and some know more about the murder than they let on.}
    
	\vspace{0.8\baselineskip}
    \begin{GmTips}[background=bgtan]
    These are all Mook NPCs but can be fleshed out more (as Henry "Rigs" Rigby) if necessary. Most likely, you will not need their stats, though, but can use them simply to add flavour and drop clues and hints.
    \end{GmTips}
    
    \subsubsection*{Henry "Rigs" Rigby}
    Bartender – Henry “Rigs” Rigby has served drinks and collected secrets at the Brass Orchid for years. A man with a sharp eye and a sharper tongue, he knows how to keep patrons talking—especially when they’ve had a few too many.
    \textbf{What He Knows:} Rigs found Edward Mercer’s missing watch tucked behind the bar, likely dropped by someone in a hurry. He can also confirm that Beatrice Langley was seen speaking with Mercer earlier in the evening.

    
	\subsubsection*{Delilah "Della" Moreau}
	Head Hostess --- Poised and perceptive, Della keeps track of the Orchid’s clientele and ensures the staff stay in line.  
	\textbf{What She Knows:} Della saw Beatrice Langley looking distraught before her performance. She had a brief but intense exchange with Mercer in a quiet corner of the club, after which she rushed backstage, visibly shaken.

	\subsubsection*{Theo Finch}
	Croupier – A professional gambler with a silver tongue, Theo oversees the Orchid’s high-stakes tables.
	\textbf{What He Knows:} Theo recalls that Mercer was in high spirits that evening, boasting about his luck finally turning. He also saw him flash a folded note to Beatrice at the bar—something that made her go pale.

	\subsubsection*{Lucian "Lucky" Calloway}
	Security Chief – A former prizefighter turned bouncer, Lucky ensures that troublemakers are swiftly escorted out.
	\textbf{What He Knows:} Lucky was managing a rowdy patron at the time of the murder and didn't see much, but he did notice Beatrice leaving Mercer’s booth looking like she'd seen a ghost. He suspects there was more to their history than either let on.

	\subsubsection*{Marguerite "Maggie" Lavoie} 
	Cabaret Singer – The star performer at the Orchid, known for her breathtaking voice and her ability to read a room.
	\textbf{What She Knows:} Maggie saw Beatrice backstage, trembling before going onstage. She also overheard her muttering about someone “never leaving well enough alone” before she downed a glass of champagne and stormed off.
\end{NPC}