\begin{WyrdScenarioHeading}[Curse of the Couch Potato]{Curse of the\\ Couch Potato}
    \label{scenario:curse-couch-potato}
    \index{Curse of the Couch Potato}
    \index{Scenario!Curse of the Couch Potato}

    It’s been a few blissfully uneventful weeks since the trailer park's last brush with animated gnome rebellion, and Dusty Pines is finally settling back into its usual bizarre routine. But the peace doesn’t last long.

    A creeping lethargy begins to overtake the park. Residents start spending entire days slumped on couches, beanbag chairs, and La-Z-Boys. At first, it’s just assumed everyone’s tired from all the recent magical drama—until they start missing meals, losing time, and murmuring about “The Great Sit.”

    Bobby “the Befuddled” Barkins is, unfortunately, among the afflicted—currently glued to his couch and watching an endless loop of daytime soap operas. With the park sliding into comfy, cushion-based chaos, it falls to the players to figure out what’s going on, resist the lure of nap time, and confront the spectral legend at the heart of the problem: Lazy Lou.

    \subsection*{Premise}
    A strange magical curse is keeping the residents of Dusty Pines trapped in their favourite seats—literally. The players must uncover the source of the enchantment, confront the ghostly slacker responsible, and free the park from the supernatural slump before Dusty Pines becomes a ghost town of glorified beanbags.

    \subsection*{Goals for the Players}
    \begin{itemize}
        \item Investigate the origin and magical mechanics of the furniture curse.
        \item Locate the remains of Lazy Lou and lay him (and his recliner) to rest.
        \item Help cursed residents overcome their supernatural laziness.
    \end{itemize}

    \subsection*{Atmosphere \& Tone}
    This scenario leans into sleepy absurdism, domestic horror, and ghostly mischief. Expect slow-motion chase scenes, snack-based temptations, and heartfelt (or snack-fueled) interventions. Let the players be weird, embrace the mundane, and remember: the longer they sit, the stronger the pull becomes.

\end{WyrdScenarioHeading}

This scenario is all about the slow slide into magical sloth. Unlike the chaos of rampaging flamingos or gnome uprisings, this curse is sneakier—it feels good. Too good. The players will face temptations of comfort, ease, and dangerously cozy furniture. Encourage the group to ham it up: dramatic sighs as they lower into chairs, inner monologues about snack cravings, or failed attempts to resist the urge to lounge. Let the humor and horror of sedentary doom play out at a languid pace—but remind them that the longer they delay, the harder it becomes to stand up again.

\subsection{The First Victim: Bobby’s Living Room Situation}

The players are summoned to Bobby’s trailer by a frantic message scratched into the back of a pizza box and delivered by Edna’s raccoon familiar, Gary. The message reads:

\begin{center}
\fbox{\parbox{0.85\linewidth}{
\centering
\textbf{\large “HELP. I CAN’T LEAVE THE COUCH. THE TV IS TOO STRONG. SEND SNACKS.”\\
– Bobby}}
}
\end{center}

Upon arrival, the players find Bobby stuck on his battered brown couch, halfway through a six-hour soap opera marathon and wrapped in three mismatched blankets. The trailer is dark, save for the flickering television and a faint magical shimmer pulsing from the couch cushions.

\subsubsection*{What’s Going On}
Bobby has been couch-bound for nearly 48 hours. Every time he tries to stand, he feels an overwhelming sense of guilt, dread, and overwhelming desire to know what happens next on \textit{Secrets of the Swamp}. Even teleportation magic fizzles near the recliner.

\begin{itemize}
    \item A successful \textbf{Lore} or \textbf{Notice} \DL{+1} detects residual ghost magic — faint, lazy, and vaguely buttery.
    \item Bobby can talk but is clearly distracted, muttering things like “the couch knows” and “Lou sees all.”
    \item There’s a suspicious old recliner in the corner. Bobby insists he got it “cheap at a cursed estate sale.”
\end{itemize}

\subsubsection*{How the Players Can Help}
\begin{itemize}
    \item \textbf{Turn off the TV:} Breaking the soap opera’s hold (or switching it to static) may weaken the curse.
    \item \textbf{Get Bobby Moving:} A strong enough emotional appeal (e.g., mentioning a snack sale at the corner store or saying Edna is about to repossess his hat) may snap him out of it.
    \item \textbf{Examine the Recliner:} It bears a worn nametag stitched into the seat: “Property of L. Lou.” Uh-oh.
\end{itemize}

\begin{CommentBox}{Optional Escalation}
If the players spend too long in the trailer, they begin to feel unusually comfy… ask for a Will check \DL{+1} or describe a creeping desire to find their own “perfect spot.”
\end{CommentBox}

\subsection{Investigating the Source of the Curse}

With Bobby semi-conscious and the recliner giving off serious “cursed object” energy, the players will need to dig deeper. The couch curse is spreading across Dusty Pines like spilled soda on shag carpet. Neighbours report being unable to leave their furniture, and others claim to have seen a hazy figure in pajamas wandering the park after midnight.

The clues all seem to point in one direction: a spectral slacker from beyond the grave… Lazy Lou.

\subsubsection*{What the Residents Say}
Interviewing the locals yields a mix of confusion, sleepy mumbling, and snack-fueled half-theories:
\begin{itemize}
    \item \textbf{Conspiracy Carl} claims the couch curse is “big furniture’s revenge” for the rise of standing desks.
    \item \textbf{Mrs. Dimple} insists she saw a ghostly man in bunny slippers floating down Lot 12 last Tuesday.
    \item \textbf{Tito the Chupacabra} has been seen napping on every recliner he can find—but denies being cursed. “It’s just ambiance,” he insists.
\end{itemize}

\subsubsection*{Magical Clues}
\begin{itemize}
    \item A \textbf{Lore} or \textbf{Investigate} \DL{+1} check near affected furniture reveals lingering ghost energy—faint, syrupy, and tinged with the scent of popcorn and regret.
    \item A successful \textbf{Empathy} \DL{+1} check with cursed residents uncovers that many of them felt drawn to sit, often hearing a whisper like: “Just five more minutes…”
    \item Hidden under one couch is a dusty, peanut-butter-smeared cassette labeled: \textit{“Lou’s Ultimate Chill Mix.”}
\end{itemize}

\subsubsection*{Lou Lore}
After a few inquiries (or a trip to Edna’s increasingly sarcastic “Curse Archives”), the players can learn:
\begin{itemize}
    \item Lazy Lou was a former Dusty Pines resident known for never leaving his recliner. He passed away sometime in the ‘90s while halfway through a bag of cheese puffs.
    \item His ashes were supposedly scattered around the park… though no one remembers where.
    \item Lou’s favourite chair, affectionately known as \textbf{“Big Bertha,”} was donated anonymously to the park’s communal rec area years ago and has since changed hands several times.
\end{itemize}

\subsubsection*{How the Players Might Proceed}
\begin{itemize}
    \item Track down all known cursed chairs and see if they share traits (lounginess, TV remote lodged in cushions, mysterious aura of indifference).
    \item Use a magical detector, dog, or disgruntled raccoon to follow ghost energy trails.
    \item Set a trap: turn on a late-night movie marathon in the middle of the park and wait to see if Lou shows up for “his stories.”
\end{itemize}

\begin{CommentBox}{Optional Complication}
    While the players investigate, they’re offered complimentary snacks and warm blankets by a group of suspiciously mellow residents calling themselves “The Sitters.” They are extremely relaxed—and deeply invested in preserving the status quo.
\end{CommentBox}


\subsection{The Couch Potato Resistance}

Not everyone in Dusty Pines wants the curse to end.

As the players dig deeper, they begin encountering a loose-knit group of enchanted residents who have fully embraced the sedentary lifestyle. They call themselves \textbf{“The Sitters.”} Lounging on porches, reclining in camping chairs, or bundled in recliners with themed throws, they hum with eerie contentment—and subtle magical energy.

They claim Lazy Lou showed them “the truth of stillness” and invite the players to join them in “The Eternal Unwind.”

\subsubsection*{What the Sitters Believe}
\begin{itemize}
    \item Life is better horizontal.
    \item “Energy is a trap invented by the waking world.”
    \item Lou speaks to them in their dreams. He encourages calm. And snacks.
    \item Movement is… suspicious.
\end{itemize}

\textbf{Leader:} A former PTA president named \textbf{Charlene} now goes by \textbf{“Chair-lene.”} She wears a bathrobe like a ceremonial sash and speaks in soothing affirmations. She’s also surprisingly persuasive and once convinced half the park to do yoga from lawn chairs.

\begin{NPC}[description={Soothing, Persuasive, Reclining with Authority}]{Chair-lene}

    Once a PTA president and part-time life coach, Charlene fully embraced Lazy Lou’s vision and rebranded herself as “Chair-lene.” Now she leads the Sitters, a resistance of cursed residents dedicated to staying horizontal. She speaks in gentle affirmations, wields warm cocoa like a weapon, and has mastered the art of motivational stillness. Chair-lene isn’t aggressive—but she’s very, very convincing.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Skilled & \textbf{Rapport} \\
        \Novice  & \textbf{Empathy}, \textbf{Will}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Calm Is Contagious] Once per scene, Chair-lene can cause hesitation or doubt in an opponent with a soothing phrase, imposing a temporary -1 to their next action if they fail a \textbf{Will} check \DL{+1}.
        \item[Comfy Cult Leader] When flanked by at least two Sitters, she gains +1 to Rapport-based rolls to persuade or stall.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=2,%
        totalmild=1,totalmoderate=0,totalsevere=0,%
    ]
\end{NPC}

\end{multicols}
\clearpage
\begin{multicols}{2}


\subsubsection*{Interacting with the Sitters}
The players may:
\begin{itemize}
    \item \textbf{Be Tempted:} The Sitters offer snacks, matching slippers, and beanbags “aligned with your aura.” Any player who sits for too long may feel the effects of the curse begin to settle in. Ask for a \textbf{Will} check \DL{+1}.
    \item \textbf{Face Resistance:} The Sitters may hide cursed objects, lie about Lou’s whereabouts, or redirect the players with cozy misdirection.
    \item \textbf{Try to Persuade Them:} Appealing to the Sitters’ pre-curse interests (bingo night, chili cook-offs, conspiracy podcasting) may help break their trance-like devotion.
\end{itemize}

\begin{NPC}[description={Cursed, Content, Collectively Couch-Bound}]{The Sitters}

    The Sitters are a loosely organized (and loosely reclined) group of Dusty Pines residents who have embraced Lazy Lou’s message of “eternal relaxation.” They wear matching pajama robes, carry embroidered throw pillows with passive-aggressive slogans, and speak in the dulcet tones of a late-night meditation podcast. While they’re not violent, they’re highly resistant to change—and unnervingly persuasive about how nice it is to just sit down for a bit.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Skilled & \textbf{Will} \\
        \Novice  & \textbf{Rapport}, \textbf{Empathy}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Group Tranquility Field] When within five feet of their “chill zone,” they project a calm aura. Anyone entering must pass a \textbf{Will} check \DL{+1} or feel overwhelming temptation to sit.
        \item[Snack-Based Loyalty] If bribed with just the right snack (e.g. pickle chips, nostalgic cereal, or gas station empanadas), their unity may falter.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=2,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}

\subsubsection*{Resolving the Conflict}
Options include:
\begin{itemize}
    \item \textbf{Reawaken Their Drive:} Use old photos, trailer gossip, or impassioned speeches to remind them who they were before “The Great Sit.”
    \item \textbf{Disrupt Their Base:} Temporarily dispel the magic around their primary gathering couch (a velvet sectional nicknamed “The Mothership”) to scatter the group’s focus.
    \item \textbf{Recruit Them:} Convince the Sitters that truly honoring Lou means helping him rest in peace. This approach earns allies for the final confrontation.
\end{itemize}


\subsection{Locating Lazy Lou’s Remains}

Rumours swirl around the park like dryer lint: Lazy Lou’s ashes were never properly scattered. According to urban legend (or a deeply confused Bobby), they were mistakenly mixed into the stuffing of a secondhand recliner... which has since moved around Dusty Pines more times than the snack truck.

Finding his final resting place is key to ending the curse—but with so many recliners and couches in circulation, it’s like tracking a ghost through a used furniture outlet.

\subsubsection*{Tracking the Recliner}
Here are a few ways players might locate the infamous cursed seat:
\begin{itemize}
    \item \textbf{Follow the Trail:} A successful \textbf{Investigate} \DL{+1} reveals a series of recliner exchanges logged in Bobby’s official “Furniture Transfer Notebook” (which is actually a takeout menu with scribbles on it).
    \item \textbf{Talk to Residents:} Several residents remember owning a strange recliner—faint ghost smells, whispers about napping, and one resident who dreamed of Lou inviting him to “the big lounge in the sky.”
    \item \textbf{Ask Edna:} For a price, Edna offers a “Lou-Sniffing Candle” that flickers when near his ashes. (It also smells like beef jerky.)
    \item \textbf{Track the Aura:} With a \textbf{Lore} \DL{+2} check or magical aid, players can follow the faint ghost energy leading to the final location of Lou’s remains.
\end{itemize}

\subsubsection*{Where the Recliner Ends Up}
The chair—\textbf{Big Bertha}—is found:
\begin{itemize}
    \item Half-buried under a tarp behind the laundry trailer.
    \item In someone’s shed, surrounded by snack wrappers and unopened mail.
    \item (Optional twist) Actively resisting—Big Bertha growls softly and vibrates when approached.
\end{itemize}

\subsubsection*{Dealing With the Remains}
To lay Lou to rest, the players must:
\begin{itemize}
    \item \textbf{Retrieve the ashes:} Hidden in a coffee can taped inside the base of the recliner.
    \item \textbf{Hold a Memorial:} A player may deliver a eulogy, play Lou’s old chill mix, or conduct a formal ceremony (bongos optional).
    \item \textbf{Convince Bertha:} If the chair is sentient, they may need to soothe, persuade, or wrestle her into letting go.
\end{itemize}

\begin{CommentBox}{Optional Climax}
The chair, infused with Lou’s last will, challenges a player to a final Sit-Off. Whoever wins gains the right to decide the fate of the curse.
\end{CommentBox}


\begin{NPC}[description={Haunted, Heavy, Deeply Resentful of Standing}]{Big Bertha (The Recliner)}

    Once a simple chair, Big Bertha now holds the heart of the couch curse. Stuffed with more than just old popcorn and remote controls, she carries the spiritual residue of Lazy Lou himself. Bertha groans when moved, growls when threatened, and has a near-hypnotic pull on anyone who sits in her. Some say she’s sentient. Others say she’s just bitter and overstuffed. Either way, she’s a force to reckon with—especially if you try to take her remote.

    \vspace{0.5\baselineskip}
    \begin{SkillsBox}
        \Skilled & \textbf{Provoke} \\
        \Novice  & \textbf{Athletics}, \textbf{Will}
    \end{SkillsBox}

    \begin{TraitsBox}
        \item[Hypnotic Comfort] Anyone who sits on Bertha must succeed at a \textbf{Will} check \DL{+2} or become momentarily cursed with the need to stay seated.
        \item[Recline and Resist] When physically threatened or moved, Bertha may buck, tip, or roll with surprising strength. Gains +1 to \textbf{Athletics} when resisting relocation.
        \item[Lou’s Echo] While within 10 feet, Bertha can channel a lazy ghost whisper: “Just five more minutes…” granting her +1 to \textbf{Provoke} once per scene.
    \end{TraitsBox}

    \DamageBox[%
        totalfatigue=2,%
        totalmild=1,totalmoderate=1,totalsevere=0,%
    ]
\end{NPC}

\subsection{Ending the Scenario}

Once Lazy Lou’s ashes have been recovered and properly laid to rest—be it with a backyard memorial, an offering of bean dip, or a flaming Viking recliner boat (highly recommended)—the lingering enchantment begins to fade.

Cursed furniture lets out long, peaceful sighs. Bobby finally stands up, blinking at the sunlight like a man reborn. The Sitters either come to their senses… or schedule weekly “gentle sit-ins” for community bonding. For the first time in days, Dusty Pines feels like itself again—just weird, not cursed.

\subsubsection*{Possible Endings}
\begin{itemize}
    \item \textbf{Peaceful Release:} Lou’s spirit waves from atop Big Bertha as it gently reclines into a puff of ghostly mist. The curse ends peacefully.
    \item \textbf{Chaotic Closure:} The Sitters go out with a bang — beanbags fly, recliners spark, and one lawn chair launches like a catapult—but in the end, freedom is restored.
    \item \textbf{Open-Ended Ending:} The curse is mostly lifted… but one loveseat keeps whispering “nap time” at midnight.
\end{itemize}

\subsubsection*{Rewards}
\begin{itemize}
    \item Bobby offers the players a free month of rent—and a coupon for half off at Edna’s “Potion of the Month Club.”
    \item Each player may take home one slightly haunted throw pillow. (Provides +1 Rapport once per session when used dramatically.)
    \item Edna leaves a congratulatory note… and a suspiciously soft recliner on their porch. It winks.
\end{itemize}

