\begin{NPC}[%
    name=Faleen Marr,%
    description=Obsessive Concord Ritualist%
  ]{Faleen Marr}
  
  \emph{A field scholar obsessed with unlocking the magic of the past—even if it consumes her.}
  
  \subsubsection*{Background:}
  Faleen Marr is a brilliant but controversial scholar within the Sapphire Concord, renowned for her knowledge of pre-imperial ritual structures and discredited theories about memory magic. This expedition is her chance to prove that the lost art of Echo Binding was real—and that it can be restored. But as the tomb responds to her presence, it becomes unclear whether Faleen is guiding the ritual… or being guided by it.
  
  \vspace{0.5\baselineskip}

  \begin{SkillsBox}
    \Expert & Perform Ritual from Fragment \\
    \Skilled & Read Untranslated Glyphs \\
    \Novice & Conceal True Motives, Resist Magical Fatigue \\
  \end{SkillsBox}

  \begin{SkillsBox}[Spells]
      \Skilled & Echo Binding (p. \pageref{spell:echo-binding}) \\
      \Novice & Read the Blood (p. \pageref{spell:read-the-blood}), Kindle Grief (p. \pageref{spell:kindle-grief}) \\
\end{SkillsBox}

  \ManaBox

  \begin{TraitsBox}
    \item[Echo Touched] — Once per session, remember something that happened to someone else—long ago, or possibly in another life.
    \item[This Is Bigger Than Us] — May escalate a scene or introduce a complication in pursuit of historical inevitability.
    \item[Unstable Focus] — If forced to defend herself, Faleen may reroll a failed action at the cost of 1 Fatigue.
  \end{TraitsBox}

  \DamageBox

\end{NPC}

