\begin{NPC}[%
    name=The Restless Priest-Queen,%
    description=Echo of the First City’s Last Voice%
  ]{The Restless Priest-Queen}
  
  \emph{A fragment of a ruler’s soul preserved in stone and silence, waiting to be remembered—or to return.}
  
  \subsubsection*{Background:}
  Once the final voice of a forgotten city, the Priest-Queen sealed her empire with a ritual of memory and silence, binding her soul into mural, echo, and ash. Her mind has drifted through time ever since—fractured yet enduring. Now awakened by Faleen Marr's ritual, she watches the players through a veil of identity and prophecy. She may view them as loyalists, traitors, or tools to restore what was hers.

  \vspace{0.5\baselineskip}

  \begin{SkillsBox}
    \Expert & Command Ghosts and Spirits \\
    \Skilled & Instill Fear with a Glance, Sense Emotional Residue \\
    \Novice & Interpret Ancient Rituals, Resist Magical Influence \\
  \end{SkillsBox}
  

  \begin{SkillsBox}[Spells]
    \Skilled & Echo Binding (p. \pageref{spell:echo-binding}), Name of Dust (p. \pageref{spell:name-of-dust}) \\
  \end{SkillsBox}

  \ManaBox

  \begin{TraitsBox}
    \item[I Am the Ending Remembered] — Once per scene, declare an event as “already foreseen” and retroactively alter a failed roll or enemy action.
    \item[To Awaken Is to Forget] — While she is active, the GM may introduce moments of memory loss, narrative gaps, or altered perception for players.
    \item[Memory Is My Domain] — Gains a bonus when interacting with spirits, past events, or magical memory echoes.
  \end{TraitsBox}

  \DamageBox

\end{NPC}


